---
title: "Analyses"
author: "Lars Schilling"
date: last-modified
date-format: "YYYY-MM-DD HH:mm:ss"
bibliography: references.bib
csl: apa.csl
editor: visual
format:
  html:
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    highlight-style: haddock
    theme: flatly
    toc: true
    toc-location: left
    embed-resources: true
execute:
  warning: false
  message: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
```

# Dependencies

```{r}
path <- "G:/Meine Ablage/Analytical_flexibility_llm_reviews/tvd_mi"

paper_llm_score_name <- "tvd_mi_scores_paper_llm_review_1.parquet"

paper_human_name <- "tvd_mi_scores_paper_human_review_2.parquet"
```

```{r}
# Flags for skipped or invalid API responses
SKIP_MESSAGE <- "Skipped cause of invalid input"
TOTAL_FAILURE_MESSAGE = "LLM call failed after multiple retries"

COMBO_COL <- c("paper_id", "model", "temperature", "reasoning_effort", "chain_of_thought", "note_taking") # Set to expected combo columns
CONFIG_COL <- c("model", "hyperparameter", "chain_of_thought", "note_taking") # Set to expected configuration columns

# Bootstrap settings
NUM_ITERATIONS <- 1000
CONFIDENCE_LVL <- 0.95

# Posthoc-test settings
ALPHA <- 0.05
POST_HOC_CORRECTION = "holm"
```

```{r, results= 'hide'}
load_pkg <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}

load_pkg("arrow")
load_pkg("tidyverse")
load_pkg("lme4")
load_pkg("car")
load_pkg("emmeans")
load_pkg("multcomp")
load_pkg("multcompView")
load_pkg("broom.mixed")
load_pkg("transport")
load_pkg("knitr")
load_pkg("kableExtra")
load_pkg("cowplot")
load_pkg("ggtext")
```

# Load data

```{r}
full_path_paper_llm <- file.path(path, paper_llm_score_name)


paper_llm_score <- read_parquet(full_path_paper_llm,
                                as_data_frame = TRUE, mmap = TRUE)

full_path_paper_human <- file.path(path, paper_human_name)

paper_human_score <- read_parquet(full_path_paper_human,
                                  as_data_frame = TRUE, mmap = TRUE)
```

# Content checks

The function creates metadata-columns which indicate weather combinations of paper and configuration have been attempted to be judged by the TVD-MI, and weather they yielded valid TPRs and FPRs in that case.

```{r}
# Helper function to clean duplicates with granular success flags
clean_duplicates_function <- function(df, 
                                      combo_cols, 
                                      tpr_col, 
                                      fpr_col, 
                                      skip_msg = SKIP_MESSAGE, 
                                      fail_msg = TOTAL_FAILURE_MESSAGE) {
  
  df_cleaned <- df |>
    mutate(
      # Create helper columns
      is_tpr_skip = .data[[tpr_col]] == skip_msg,
      is_fpr_skip = .data[[fpr_col]] == skip_msg,
      is_tpr_fail = .data[[tpr_col]] == fail_msg,
      is_fpr_fail = .data[[fpr_col]] == fail_msg,
      is_tpr_valid = !(.data[[tpr_col]] %in% c(skip_msg, fail_msg)),
      is_fpr_valid = !(.data[[fpr_col]] %in% c(skip_msg, fail_msg))
    ) |>
    mutate(
      # Assign quality tiers for prioritizing
      quality_tier = case_when(
        is_tpr_valid & is_fpr_valid ~ 1,
        (is_tpr_fail & is_fpr_valid) | (is_fpr_fail & is_tpr_valid) ~ 2,
        is_tpr_fail & is_fpr_fail ~ 3,
        (is_tpr_skip & is_fpr_valid) | (is_fpr_skip & is_tpr_valid) ~ 4,
        (is_tpr_skip & is_fpr_fail) | (is_fpr_skip & is_tpr_fail) ~ 5,
        is_tpr_skip & is_fpr_skip ~ 6,
        TRUE ~ 7
      ),
      .orig_idx = row_number()
    ) |>
    # Select highest tier for each paper-configuration combo
    group_by(pick(all_of(combo_cols))) |>
    arrange(quality_tier, .orig_idx, .by_group = TRUE) |>
    slice(1) |>
    ungroup() |>
    # Drop helper columns
    dplyr::select(-any_of(c(".orig_idx", "is_tpr_skip", "is_fpr_skip", "is_tpr_fail", "is_fpr_fail", "is_tpr_valid", "is_fpr_valid")))
  
  return(df_cleaned)
}
```

```{r}
paper_llm_score_cld <- clean_duplicates_function(paper_llm_score,
                                                 COMBO_COL,
                                                 "tpr_avg_tvd_mi_score",
                                                 "fpr_avg_tvd_mi_score")

paper_human_score_cld <- clean_duplicates_function(paper_human_score,
                                                  "paper_id",
                                                  "tpr_avg_tvd_mi_score",
                                                  "fpr_avg_tvd_mi_score")
```

# Completness checks

Incomplete or frequently skipped/invalid combinations papers, configurations and combinations are not dropped, but in case the following indicates odd results these will be taken into consideration in the result interpretation.

## LLM-authored reviews

### Status summary global:

```{r}
paper_llm_score_cld |>
  summarize(
    `Total Combinations` = n(),
    `Both Valid (Full Success)` = sum(quality_tier == 1),
    `Valid + Fail` = sum(quality_tier == 2),
    `Both Fail` = sum(quality_tier == 3),
    `Valid + Skip` = sum(quality_tier == 4),
    `Fail + Skip` = sum(quality_tier == 5),
    `Both Skip` = sum(quality_tier == 6),
    .groups = "drop"
  ) |>
  mutate(
    `Success rate` = paste0(round((`Both Valid (Full Success)` / `Total Combinations`) * 100, 1), "%")
  ) |>
  kable(format = "html", align = "r") |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = F
  )
```

### Status Summary by configuration:

```{r}
paper_llm_score_cld |>
  group_by(model, temperature, reasoning_effort, chain_of_thought, note_taking) |>
  summarize(
    `Total amount of papers` = n(),
    `Both Valid (Full Success)` = sum(quality_tier == 1),
    `Valid + Fail` = sum(quality_tier == 2),
    `Both Fail` = sum(quality_tier == 3),
    `Valid + Skip` = sum(quality_tier == 4),
    `Fail + Skip` = sum(quality_tier == 5),
    `Both Skip` = sum(quality_tier == 6),
    .groups = "drop"
  ) |>
  mutate(
    `Success rate` = paste0(round((`Both Valid (Full Success)` / `Total amount of papers`) * 100, 1), "%")
  ) |>
  arrange(desc(`Both Valid (Full Success)` / `Total amount of papers`)) |> 
  kable(format = "html", align = "r") |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = F
  ) |> 
  scroll_box(width = "100%", height = "400px")
```

### Status summary by paper:

```{r}
paper_llm_score_cld |>
  group_by(`Paper ID` = paper_id) |>
  summarize(
    `Total amount of configurations` = n(),
    `Both Valid (Full Success)` = sum(quality_tier == 1),
    `Valid + Fail` = sum(quality_tier == 2),
    `Both Fail` = sum(quality_tier == 3),
    `Valid + Skip` = sum(quality_tier == 4),
    `Fail + Skip` = sum(quality_tier == 5),
    `Both Skip` = sum(quality_tier == 6),
    .groups = "drop"
  ) |>
  mutate(
    `Success rate` = paste0(round((`Both Valid (Full Success)` / `Total amount of configurations`) * 100, 1), "%")
  ) |>
  arrange(desc(`Both Valid (Full Success)` / `Total amount of configurations`)) |> 
  kable(format = "html", align = "r") |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = F
  ) |> 
  scroll_box(width = "100%", height = "400px")
```

## Human-authored reviews

### Status summary by paper:

```{r}
paper_human_score_cld |>
  group_by(`Paper ID` = paper_id) |>
  summarize(
    `Total amount of configurations` = n(),
    `Both Valid (Full Success)` = sum(quality_tier == 1),
    `Valid + Fail` = sum(quality_tier == 2),
    `Both Fail` = sum(quality_tier == 3),
    `Valid + Skip` = sum(quality_tier == 4),
    `Fail + Skip` = sum(quality_tier == 5),
    `Both Skip` = sum(quality_tier == 6),
    .groups = "drop"
  ) |>
  mutate(
    `Success rate` = paste0(round((`Both Valid (Full Success)` / `Total amount of configurations`) * 100, 1), "%")
  ) |>
  arrange(desc(`Both Valid (Full Success)` / `Total amount of configurations`)) |> 
  kable(format = "html", align = "r") |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = F
  ) |> 
  scroll_box(width = "100%", height = "400px")
```

# Calculations

## Score transformation and calculations

The `total_score` column contains the final TVD-MI metric. The new column `hyperparameter` combines the information for temperature parameter or reasoning effort parameter. The mean success rate and the mean TVD-MI per configuration group are calculated. For the human data, the success rate is by definition set to 1.

```{r}
# 1. Human Data Processing (Baseline)
paper_human_processed <- paper_human_score_cld |> 
  mutate(paper_id = as.factor(paper_id)) |> 
  mutate(across(contains("score"), ~ suppressWarnings(as.numeric(.)))) |> 
  mutate(
    tvd_mi_score = (tpr_avg_tvd_mi_score - fpr_avg_tvd_mi_score),
    
    # Success rates (Metric 1); Human validity is 100% by definition
    success_rate = 1,
    
    # Performance means (Metric 2 and 3)
    group_mean = if(all(is.na(tvd_mi_score))) NA_real_ else mean(tvd_mi_score, na.rm = TRUE),

  ) |> 
  rename_with(~ paste0(., "_human"), .cols = -c(paper_id)) |> 
  mutate(config_label_human = "Human_Global")

# 2. LLM Data Processing (Config-Level)
paper_llm_processed <- paper_llm_score_cld |> 
  mutate(paper_id = as.factor(paper_id)) |> 
  mutate(across(contains("score"), ~ suppressWarnings(as.numeric(.)))) |> 
  mutate(
    model = case_match(
      model,
      "gpt-5-mini-2025-08-07" ~ "GPT-5 Mini",
      "gpt-5-nano-2025-08-07" ~ "GPT-5 Nano",
      "gpt-4o-2024-08-06" ~ "GPT-4o",
      "gpt-4o-mini-2024-07-18" ~ "GPT-4o Mini",
      "o4-mini-2025-04-16" ~ "o4 Mini",
      "o3-mini-2025-01-31" ~ "o3 Mini",
      "gpt-3.5-turbo-0125" ~ "GPT-3.5 Turbo",
      "llama-3.3-70b-versatile" ~ "Llama 3.3 (70B)",
      "gemini-3-flash-preview" ~ "Gemini-3 Flash",
      .default = model
    ),
    hyperparameter = case_when(
      !is.na(reasoning_effort) ~ paste0("Re ", reasoning_effort),
      !is.na(temperature) ~ paste0("Tempr ", temperature),
      TRUE ~ "default"
    ),
    chain_of_thought = case_match(
      chain_of_thought,
      "Explain your thought process step by step." ~ "True",
      NA ~ "False",
      .default = chain_of_thought
    ),
    note_taking = case_match(
      note_taking,
      "No" ~ "Active",
      "Yes" ~ "Not active",
      .default = note_taking
    )
  ) |> 
  mutate(
    tvd_mi_score = (tpr_avg_tvd_mi_score - fpr_avg_tvd_mi_score),
    ) |> 
  unite("temp_config_str", all_of(CONFIG_COL), sep = "_", remove = FALSE) |> 
  mutate(
    config_id = as.numeric(factor(temp_config_str, levels = unique(temp_config_str))),
    config_label = paste0("Config_", config_id)
  ) |> 
  dplyr::select(-temp_config_str) |> 
  group_by(config_label) |> 
  mutate(
    # Success rates (Metric 1)
    success_rate     = mean(is_created, na.rm = TRUE),

    # Performance means (Metric 2)
    group_mean = if(all(is.na(tvd_mi_score))) NA_real_ else mean(tvd_mi_score, na.rm = TRUE),
  ) |> 
  ungroup() |>
  left_join(paper_human_processed |> 
              dplyr::select(
                paper_id,
                success_rate_human,
                tvd_mi_score_human,
                group_mean_human
              ),
            by = "paper_id"
  )

# 3. Summary table
summary_table <- paper_llm_processed |> 
  group_by(config_id) |> 
  summarize(
    
    # Success
    mean_success_rate     = first(success_rate),
    
    # Performance (Mean)
    mean_score     = first(group_mean),
    
    .groups = "drop"
  )
```

## Bootstraping

The bootstrap creates 1000 independent possible score distributions per configuration group for the success metric and the TVD-MI metric. Values at half the alpha level are extracted as lower and upper bounds.

```{r}
# Configuration
num_iterations <- NUM_ITERATIONS
confidence_lvl <- CONFIDENCE_LVL
global_alpha <- (1 - confidence_lvl) / 2

# Helper function
bootstrap_function <- function(df, 
                              group_col,
                              score_col,
                              is_created_col = NULL, # Optional
                              iterations = num_iterations, 
                              alpha = global_alpha,
                              calc_success = FALSE) {
  
  set.seed(42)
  
  boot_distribution <- map_df(1:iterations, function(i) {
    df |> 
      group_by(.data[[group_col]]) |> 
      slice_sample(prop = 1, replace = TRUE) |> 
      summarise(
        # Plot 1: Success
        boot_success = if (calc_success) {
          mean(.data[[is_created_col]], na.rm = TRUE)
        } else {
          NA_real_
        },
        
        # Plot 2: Performance
        boot_mean = mean(.data[[score_col]], na.rm = TRUE),
        
        .groups = "drop"
      )
  })
  
  # Calculate quantiles
  ci_results <- boot_distribution |> 
    group_by(.data[[group_col]]) |> 
    summarise(
      across(starts_with("boot_"), 
             list(lower = ~quantile(.x, alpha, na.rm = TRUE),
                  upper = ~quantile(.x, 1 - alpha, na.rm = TRUE)),
             .names = "{.col}_{.fn}"),
      .groups = "drop"
    )
  
  # Delete empty columns
  if (!calc_success) {
    ci_results <- ci_results |> dplyr::select(-starts_with("boot_success"))
  }
  
  return(ci_results)
}
```

```{r}
llm_boot_summary <- bootstrap_function(
  df = paper_llm_processed,
  group_col = "config_label",
  score_col = "tvd_mi_score",
  is_created_col = "is_created",
  calc_success = TRUE
)

human_boot_summary <- bootstrap_function(
  df = paper_human_processed,
  group_col = "config_label_human",
  score_col = "tvd_mi_score_human",
)
```

```{r}
paper_llm_processed_bind <- paper_llm_processed |> 
  left_join(llm_boot_summary, by = "config_label") |> 
  cross_join(
    human_boot_summary |>
      dplyr::select(-config_label_human) |> 
      rename_with(~ paste0(.x, "_human")))
```

## Plot preparation

For the specification curve plots the configuration columns are formated.

```{r}
data_plot <- paper_llm_processed_bind |> 
  mutate(
    model = fct_relevel(
      as.factor(model),
      "Gemini-3-Flash", "Llama 3.3 (70B)", "GPT-3.5 Turbo", "o3 Mini", 
      "o4 Mini", "GPT-4o Mini", "GPT-4o", "GPT-5 Nano", "GPT-5 Mini"
    ),
    hyperparameter = fct_relevel(
      as.factor(hyperparameter),
      "Tempr 1.5", "Tempr 1", "Tempr 0.5", "Tempr 0", "Re high", "Re low"
    ),
    chain_of_thought = fct_relevel(
      as.factor(chain_of_thought),
      "True", "False"
    ),
    note_taking = fct_relevel(
      as.factor(note_taking),
      "Active", "Not active"
    )
  ) |> 
  rename(
    `Model` = model,
    `Hyper-<br> parameter` = hyperparameter,
    `CoT<br> used` = chain_of_thought,
    `Notes` = note_taking
  )
```

# Plots

## Function

The plot function for a specification curve is taken from [@cumminsThreatAnalyticFlexibility2025]:

```{r}
specification_curve_plot_with_shading <- function(data,
                                                  outcome = "outcome",
                                                  outcome_name = "Outcome",
                                                  is_processed = NULL,
                                                  plot_title = NULL,
                                                  interval_lower = NULL,
                                                  interval_upper = NULL,
                                                  rank_by = "rank",
                                                  rank_by_outcome = FALSE,
                                                  relative_height_of_upper_plot = 0.70,
                                                  outcome_cutoff = NULL,
                                                  facet_by = NULL,
                                                  facet_ncol = 2,
                                                  shade_lower = NULL,
                                                  shade_upper = NULL,
                                                  shade_fill_by = NULL,
                                                  shade_values = NULL,
                                                  shade_alpha = 0.5,
                                                  shade_fill_constant = "red",
                                                  mutate_plots = NULL) {
  require(dplyr)
  require(tidyr)
  require(ggplot2)
  require(cowplot)
  require(ggtext)
  require(rlang)
  require(grid)
  
  data <- data |>
    rename(outcome = {{outcome}}, rank = {{rank_by}})
  
  # REFINEMENT
  if (rlang::quo_is_null(rlang::enquo(is_processed)) || rlang::quo_is_missing(rlang::enquo(is_processed))) {
    data <- data |> mutate(is_processed = 1.0)
  } else {
    data <- data |> mutate(is_processed = {{is_processed}})
  }
  
  if (!is.null(interval_lower))
    data <- data |> rename(interval_lower = {{interval_lower}})
  else
    data$interval_lower <- data$outcome
  if (!is.null(interval_upper))
    data <- data |> rename(interval_upper = {{interval_upper}})
  else
    data$interval_upper <- data$outcome
  
  if (rank_by_outcome)
    data <- data |> arrange(outcome) |> mutate(rank = dplyr::row_number())
  
  keep_num <- c("rank", "outcome", "interval_lower", "interval_upper", "is_processed")
  if (!is.null(shade_lower))
    keep_num <- c(keep_num, as_name(ensym(shade_lower)))
  if (!is.null(shade_upper))
    keep_num <- c(keep_num, as_name(ensym(shade_upper)))
  
  data <- data |> mutate(across(.cols = -all_of(keep_num), .fns = as.factor))
  exclude_cols_base <- keep_num
  
  facet_name <- NULL
  if (!is.null(facet_by)) {
    facet_sym  <- ensym(facet_by)
    facet_name <- as_name(facet_sym)
    if (!facet_name %in% names(data))
      stop("facet_by column not found in data.")
  }
  
  # specify column that controls fill (will be facet)
  if (!is.null(shade_fill_by)) {
    fill_name <- as_name(ensym(shade_fill_by))
  } else {
    fill_name <- facet_name
  }
  if (!is.null(fill_name))
    exclude_cols_base <- c(exclude_cols_base, fill_name)
  
  # resolve global fill levels & colors (so colors are consistent across facets)
  fill_levels <- if (!is.null(fill_name))
    levels(droplevels(as.factor(data[[fill_name]])))
  else
    NULL
  resolved_fill <- NULL
  if (!is.null(fill_levels) && !is.null(shade_values)) {
    if (!is.null(names(shade_values)) &&
        any(nzchar(names(shade_values)))) {
      resolved_fill <- shade_values[fill_levels]
    } else {
      resolved_fill <- rep(shade_values, length.out = length(fill_levels))
      names(resolved_fill) <- fill_levels
    }
  }
  
  build_one <- function(df,
                        title_text = plot_title,
                        show_y_titles = TRUE) {
    
    # REFINEMENT: Ensure rank order for smooth ribbon rendering
    df <- df |> arrange(rank)
    
    p_estimates <- df |>
      mutate(outcome_name = outcome_name) |>
      ggplot(aes(rank, outcome))
    
    # shaded band behind points/intervals
    if (!is.null(shade_lower) && !is.null(shade_upper)) {
      lower_sym <- ensym(shade_lower)
      upper_sym <- ensym(shade_upper)
      
      band <- df |>
        summarise(
          ymin = dplyr::first(!!lower_sym),
          ymax = dplyr::first(!!upper_sym),
          .groups = "drop"
        )
      
      if (!is.null(fill_name) && fill_name %in% names(df)) {
        band$.__fill <- dplyr::first(df[[fill_name]])
        p_estimates <- p_estimates +
          geom_rect(
            data = band,
            aes(
              xmin = -Inf,
              xmax = Inf,
              ymin = ymin,
              ymax = ymax,
              fill = .__fill
            ),
            alpha = shade_alpha,
            inherit.aes = FALSE,
            show.legend = FALSE
          )
        if (!is.null(resolved_fill)) {
          p_estimates <- p_estimates + scale_fill_manual(values = resolved_fill, guide = "none")
        }
      } else {
        p_estimates <- p_estimates +
          geom_rect(
            data = band,
            aes(
              xmin = -Inf,
              xmax = Inf,
              ymin = ymin,
              ymax = ymax
            ),
            fill = shade_fill_constant,
            alpha = shade_alpha,
            inherit.aes = FALSE,
            show.legend = FALSE
          )
      }
      # ensure band is within the y-scale
      p_estimates <- p_estimates + expand_limits(y = c(band$ymin, band$ymax))
    }
    
    # REFINEMENT: Shaded Ribbon CI instead of linerange
    p_estimates <- p_estimates +
      geom_ribbon(aes(ymin = interval_lower, ymax = interval_upper), 
                  fill = "#ADD8E6", alpha = 0.4) +
      geom_point(aes(alpha = is_processed), shape = "circle", size = 2) + # REFINEMENT
      scale_alpha_continuous(range = c(0.4, 1.0), guide = "none") +
      facet_grid(
        outcome_name ~ .,
        space = "free_y",
        scales = "free_y",
        switch = "y"
      ) +
      scale_y_continuous(breaks = scales::pretty_breaks()) +
      scale_x_continuous(NULL, expand = c(.02, .02)) +
      ylab(if (show_y_titles)
        "Simulation results"
        else
          NULL) +
      theme_minimal() +
      theme(
        legend.position   = "none",
        axis.line.x       = element_blank(),
        strip.placement   = "outside",
        strip.background  = element_rect(fill = NA, colour = NA),
        panel.spacing.x   = unit(0.15, "cm"),
        strip.text.y.left = if (show_y_titles)
          ggtext::element_markdown(
            angle = 90,
            face = "bold",
            size = 7,
            margin = margin(r = 20, l = 5) # REFINEMENT
          )
        else
          element_blank(),
        axis.text.y       = element_text(
          angle = 0,
          hjust = 0.5,
          size = 6
        ),
        axis.title.y      = if (show_y_titles)
          element_text(
            size = 9,
            face = "bold",
            margin = margin(r = 4)
          )
        else
          element_blank(),
        panel.spacing     = unit(0.25, "lines"),
        axis.title.x      = element_blank(),
        axis.text.x       = element_blank(),
        axis.ticks.x      = element_blank()
      )
    
    if (!is.null(outcome_cutoff)) {
      p_estimates <- p_estimates + geom_hline(yintercept = outcome_cutoff, linetype = "dashed") # REFINEMENT
    }
    
    exclude_cols <- exclude_cols_base
    if (!is.null(facet_name))
      exclude_cols <- c(exclude_cols, facet_name)
    
    p_specs <- df |>
      tidyr::pivot_longer(cols = -dplyr::all_of(exclude_cols)) |>
      arrange(rank) |>
      ggplot(aes(
        x = rank,
        y = factor(value),
        color = name
      )) +
      geom_point(size = 3.5, shape = "|") +
      facet_grid(name ~ .,
                 space = "free_y",
                 scales = "free_y",
                 switch = "y") +
      guides(color = "none") +
      scale_x_continuous(NULL, expand = c(.02, .02)) +
      ylab(if (show_y_titles)
        "Simulation conditions"
        else
          NULL) +
      theme_minimal() +
      theme(
        strip.placement   = "outside",
        strip.background  = element_rect(fill = NA, colour = NA),
        panel.spacing.x   = unit(0.15, "cm"),
        strip.text.y.left = if (show_y_titles)
          ggtext::element_markdown(
            angle = 90,
            face = "bold",
            size = 7,
            # REFINEMENT:
            lineheight = 0.9,
            margin = margin(r = 20, l = 5)
          )
        else
          element_blank(),
        axis.text.y       = element_text(
          angle = 0,
          hjust = 1,
          size = 6
        ),
        axis.title.y      = if (show_y_titles)
          element_text(
            size = 9,
            face = "bold",
            margin = margin(r = 4)
          )
        else
          element_blank(),
        panel.spacing     = unit(0.25, "lines"),
        axis.title.x      = element_blank(),
        axis.text.x       = element_blank(),
        axis.ticks.x      = element_blank()
      ) +
      scale_color_brewer(palette = "Dark2")
    
    if (is.function(mutate_plots)) {
      out <- mutate_plots(p_estimates, p_specs, df)
      if (inherits(out, "gg")) {
        p_estimates <- out
      } else if (is.list(out)) {
        if (length(out) >= 1)
          p_estimates <- out[[1]]
        if (length(out) >= 2)
          p_specs     <- out[[2]]
      }
    }
    
    g_est <- ggplotGrob(p_estimates)
    g_spc <- ggplotGrob(p_specs)
    max_w <- unit.pmax(g_est$widths, g_spc$widths)
    g_est$widths <- max_w
    g_spc$widths <- max_w
    
    combo <- cowplot::plot_grid(
      g_est,
      g_spc,
      axis = "bltr",
      align = "v",
      ncol = 1,
      rel_heights = c(relative_height_of_upper_plot, 1)
    )
    if (!is.null(title_text)) {
      title_grob <- cowplot::ggdraw() +
        cowplot::draw_label(
          title_text,
          x = 0.5,
          hjust = 0.5,
          y = 0.5, # REFINEMENT
          vjust = 0.5, # REFINEMENT
          fontface = "bold"
        )
      combo <- cowplot::plot_grid(title_grob,
                                  combo,
                                  ncol = 1,
                                  rel_heights = c(0.15, 1)) # REFINEMENT
    }
    combo
  }
  
  if (is.null(facet_by))
    return(build_one(data, plot_title, show_y_titles = TRUE))
  
  facet_vals <- if (is.factor(data[[facet_name]]))
    levels(droplevels(data[[facet_name]]))
  else
    unique(data[[facet_name]])
  plotlist <- lapply(seq_along(facet_vals), function(i) {
    v  <- facet_vals[i]
    df <- dplyr::filter(data, .data[[facet_name]] == v)
    if (nrow(df) == 0)
      return(NULL)
    local_title <- if (!is.null(plot_title))
      paste0(plot_title, ": ", v)
    else
      paste0(facet_name, ": ", v)
    is_left_col <- ((i - 1) %% facet_ncol) == 0
    build_one(df, local_title, show_y_titles = is_left_col)
  })
  plotlist <- Filter(Negate(is.null), plotlist)
  
  cowplot::plot_grid(plotlist = plotlist,
                     ncol = facet_ncol,
                     align = "hv")
}
```

## Success rate

This plot shows for how many papers in a given parameter combination the review generation was successful.

```{r}
success_spec_plot <- data_plot |>  
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyper-<br> parameter`, 
    `CoT<br> used`, 
    `Notes`,
    success_rate,
    boot_success_lower,      
    boot_success_upper
  ) |>  
  # Summarize
  group_by(Model, `Hyper-<br> parameter`, `CoT<br> used`, Notes) |>
  summarise(
    success_rate = mean(success_rate),
    boot_success_lower = mean(boot_success_lower),
    boot_success_upper = mean(boot_success_upper),
    .groups = "drop"
  ) |> 
  arrange(success_rate) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
  outcome = success_rate,
  outcome_name = "Mean success rate",
  plot_title = "Mean success rate by configuration",
  interval_lower = "boot_success_lower",
  interval_upper = "boot_success_upper",
  rank_by = rank,
  
  mutate_plots = \(top, bottom, df) {
    list(top + coord_cartesian(ylim = c(0, 1)))
  }
)

success_spec_plot

ggsave(
  filename = "output/success_spec_plot.png", 
  plot = success_spec_plot, 
  width = 10, 
  height = 8, 
  dpi = 300
)
```

## Mean

This plot indicates the average quality of LLM-authored reviews (as indicated by the TVD-MI score) for each parameter combination. Note that this plot does not consider for how many of the papers a parameter combination yielded a successful review generation in the first place.

```{r}
mean_spec_plot <- data_plot |> 
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyper-<br> parameter`, 
    `CoT<br> used`, 
    `Notes`,
    group_mean,
    boot_mean_lower, 
    boot_mean_upper,
    boot_mean_lower_human, 
    boot_mean_upper_human
  ) |> 
  # Summarize
  group_by(Model, `Hyper-<br> parameter`, `CoT<br> used`, Notes) |> 
  summarize(
    group_mean = mean(group_mean),,
    boot_mean_lower = mean(boot_mean_lower),
    boot_mean_upper = mean(boot_mean_upper),
    boot_mean_lower_human = mean(boot_mean_lower_human),
    boot_mean_upper_human = mean(boot_mean_upper_human),
    .groups = "drop"
  ) |> 
  arrange(group_mean) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
    # Basic content
    outcome = group_mean,
    outcome_name = "Mean TVD-MI score",
    plot_title = "Mean TVD-MI score by Configuration",
    interval_lower = "boot_mean_lower",
    interval_upper = "boot_mean_upper",
    rank_by = rank,
    # CI base
    shade_lower = "boot_mean_lower_human",
    shade_upper = "boot_mean_upper_human",
    
    mutate_plots = \(top, bottom, df) {
      list(top + coord_cartesian(ylim = c(-1, 1)))
    }
  )

mean_spec_plot

ggsave(
  filename = "output/mean_spec_plot.png", 
  plot = mean_spec_plot, 
  width = 10, 
  height = 8, 
  dpi = 300
)
```

# Inferential tests

The linear mixed model tests for significant differences between factor levels, e.g. the different models, in their final TVD-MI score. Note that, once again, the analysis does not consider for how many of the papers the review generation was successful. In case a factor has significant differences across its levels, a post-hoc tests investigates the level orders.

```{r}
# Function for conditional posthoc tests
conditional_posthoc_function <- function(model, alpha = 0.05, adjust = "bonferroni") {
  
  # Check if model is binomial (glmer) or linear (lmer)
  is_glmer <- inherits(model, "glmerMod")
  test_stat <- if(is_glmer) "Chisq" else "F"
  
  anova_res <- tryCatch({
    car::Anova(model, type = "II", test.statistic = test_stat)
  }, error = function(e) {
    message("ANOVA failed: ", e$message)
    return(NULL)
  })
  
  if(is.null(anova_res)) return(NULL)
  
  # Identify the p-value column (it's either Pr(>Chisq) or Pr(>F))
  p_col <- grep("Pr\\(>", colnames(anova_res), value = TRUE)
  
  # Handle cases where no terms are significant
  sig_mask <- anova_res[[p_col]] < alpha
  terms <- rownames(anova_res)
  terms <- terms[!terms %in% c("(Intercept)", "Residuals")]
  
  if(length(terms) == 0) {
    message("No significant terms found at alpha ", alpha)
    return(list(anova = anova_res, posthoc = list()))
  }
  
  # Run post-hoc tests
  results <- lapply(terms, function(term) {

    spec_formula <- as.formula(paste("~", term))
    
    # Calculate Estimated Marginal Means
    emm <- emmeans::emmeans(model, specs = spec_formula, type = "response")
    
    # Compact Letter Display (CLD)
    multcomp::cld(emm, 
                  alpha = alpha, 
                  Letters = c(letters, LETTERS), 
                  adjust = adjust, 
                  reversed = TRUE) |> 
      as.data.frame() |> 
      mutate(term = term)
  })
  
  names(results) <- terms
  return(list(anova = anova_res, posthoc = results))
}
```

```{r}
lmm_mean_total <- lme4::lmer(tvd_mi_score ~ model + hyperparameter + chain_of_thought + note_taking + (1 | paper_id),
                             data = paper_llm_processed)
posthoc_mean_total <- conditional_posthoc_function(lmm_mean_total, alpha = ALPHA, adjust = POST_HOC_CORRECTION)
```

```{r}
posthoc_mean_total
```

# Session info

```{r}
sessionInfo()
```

# References

::: {#refs}
:::
