---
title: "Analyses"
author: "Lars Schilling"
bibliography: references.bib
csl: apa.csl
editor: visual
format:
  html:
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    highlight-style: haddock
    theme: flatly
    toc: true
    toc-location: left
    embed-resources: true
execute:
  warning: false
  message: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
```


# Dependencies

```{r}
working_dir <- "G:/Meine Ablage/Thesis/tvd_mi/"

paper_llm_score_name <- "tvd_mi_scores_paper_llm_review_1.parquet"

paper_human_name <- "tvd_mi_scores_paper_human_review_2.parquet"
```

```{r}
# Flags for skipped or invalid API responses
SKIP_MESSAGE <- "Skipped cause of invalid input"
TOTAL_FAILURE_MESSAGE = "LLM call failed after multiple retries"

AMOUNT_SETTINGS <- 112 # Set to expected amount of configuration setting
AMOUNT_PAPERS <- 98 # Set to expected amount of parsed papers

COMBO_COL <- c("paper_id", "model", "temperature", "reasoning_effort", "chain_of_thought", "scope") # Set to expected combo columns
CONFIG_COL <- c("model", "hyperparameter", "chain_of_thought", "scope") # Set to expected configuration columns
BASE_SCORE_COLS <- c(
  "tpr_tvd_mi_score_1", "tpr_tvd_mi_score_2", "tpr_avg_tvd_mi_score",
  "fpr_tvd_mi_score_1", "fpr_tvd_mi_score_2", "fpr_avg_tvd_mi_score"
) # Set to expected score columns
CLEAN_SCORE_COLS <- c(
  "TPR 1", "TPR 2", "TPR AVG", 
  "FPR 1", "FPR 2", "FPR AVG"
) # Set to wanted score labels
TOTAL_SCORE_COL <- "total_score" # Set to created total score column

# Bootstrap settings
NUM_ITERATIONS <- 1000
CONFIDENCE_LVL <- 0.95

# Posthoc-test settings
###! Holmes-correction was not possible. Should I switch to bonferroni, Tuckey or try another way to run post-hoc tests?
ALPHA <- 0.05
POST_HOC_CORRECTION = "bonferroni"
```

```{r}
load_pkg <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}

load_pkg("arrow")
load_pkg("tidyverse")
load_pkg("lme4")
load_pkg("car")
load_pkg("emmeans")
load_pkg("multcomp")
load_pkg("multcompView")
load_pkg("broom.mixed")
load_pkg("transport")
load_pkg("knitr")
load_pkg("kableExtra")
load_pkg("cowplot")
load_pkg("ggtext")
```

# Load data

```{r}
full_path_paper_llm <- file.path(working_dir, paper_llm_score_name)


paper_llm_score <- read_parquet(full_path_paper_llm,
                                as_data_frame = TRUE, mmap = TRUE)

full_path_paper_human <- file.path(working_dir, paper_human_name)

paper_human_score <- read_parquet(full_path_paper_human,
                                  as_data_frame = TRUE, mmap = TRUE)
```

# Content checks

As multiple runs of APIs possibly created duplicate paper/configuration pairs, these have to be cleaned first. Besides that, the function creates metadata-columns which indicate weather combinations of paper and configuration have been attempted and yielded valid TPRs and FPRs.

```{r}
# Helper function to clean duplicates with granular success flags
clean_duplicates_function <- function(df, 
                                      combo_cols, 
                                      tpr_col, 
                                      fpr_col, 
                                      skip_msg = SKIP_MESSAGE, 
                                      fail_msg = TOTAL_FAILURE_MESSAGE) {
  
  df_cleaned <- df |>
    mutate(
      # Individual validity for the sub-metrics
      is_valid_tpr = !(.data[[tpr_col]] %in% c(skip_msg, fail_msg)),
      is_valid_fpr = !(.data[[fpr_col]] %in% c(skip_msg, fail_msg)),
      
      # The TVD-MI is only valid if BOTH are valid (Success of the TVD-MI score)
      is_valid = is_valid_tpr & is_valid_fpr,
      
      # Fail and skip flags for the compelete tier list
      is_failed  = (.data[[tpr_col]] %in% fail_msg | .data[[fpr_col]] %in% fail_msg),
      is_skipped = (.data[[tpr_col]] %in% skip_msg & .data[[fpr_col]] %in% skip_msg)
    ) |>
    mutate(
      quality_tier = case_when(
        is_valid   ~ 1, # Both TPR and FPR are clean
        is_failed  ~ 2, # Judge error
        is_skipped ~ 3, # Review generation error
        TRUE       ~ 4
      ),
      .orig_idx = row_number()
    ) |>
    group_by(pick(all_of(combo_cols))) |>
    arrange(quality_tier, .orig_idx, .by_group = TRUE) |>
    slice(1) |>
    ungroup() |>
    dplyr::select(-any_of(c(".orig_idx")))
  
  return(df_cleaned)
}
```

```{r}
paper_llm_score_cld <- clean_duplicates_function(paper_llm_score,
                                                 COMBO_COL,
                                                 "tpr_avg_tvd_mi_score",
                                                 "fpr_avg_tvd_mi_score")

paper_human_score_cld <- clean_duplicates_function(paper_human_score,
                                                  "paper_id",
                                                  "tpr_avg_tvd_mi_score",
                                                  "fpr_avg_tvd_mi_score")
```

Now the completeness of paper/configuration pairs can be checked.

## LLM-authored reviews

The first table shows the amount of processed configurations per paper for all papers who have not been processed comepletly.
The second table shows the amount of processed papers per configurations for all configurations who have not been processed comepletly.
The third table is a summary of how many combination of paper and configuration have been processed and what success status they reached.
The fourth table gives out the amount of processed papers and their success status for each configuration.
The fifth table givous out the amount of processed configurations and their success status for each paper.

###! I feel like all of these tables are a bit to much. I would prefer to keep the summary only. What do you think?

```{r}
# Any incompletly processed papers?
paper_llm_score_cld |> 
  count(`Paper ID` = paper_id) |> 
  filter(n != AMOUNT_SETTINGS) |> 
  rename(`Amount of processed configurations` = n) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# Any incompletely processsed configurations?
paper_llm_score_cld |> 
  group_by(Model = model, Temperature = temperature, `Reasoning effort` = reasoning_effort,
           CoT = chain_of_thought, `Scope` = scope, ) |> 
  summarize(row_count = n(),
            .groups = "drop") |> 
  filter(row_count != AMOUNT_PAPERS) |>
  rename(`Amount of processed papers` = row_count) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# Global
paper_llm_score_cld |>
  summarize(
    `Total amount of combinations` = n(),
    `Amount of valid results` = sum(is_valid),
    `Amount of failed results`  = sum(is_failed),
    `Amount of skipped results` = sum(is_skipped),
    .groups = "drop"
  ) |>
  mutate(`Success rate`= paste0(round((`Amount of valid results` / `Total amount of combinations`) * 100, 1), "%")) |>
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F)  
  
# By configuration
paper_llm_score_cld |>
  group_by(model, temperature, reasoning_effort, chain_of_thought, scope) |>
  summarize(
    `Total amount of papers` = n(),
    `Amount of valid results` = sum(is_valid),
    `Amount of failed results`  = sum(is_failed),
    `Amount of skipped results` = sum(is_skipped),
    .groups = "drop"
  ) |>
  mutate(`Success rate` = paste0(round((`Amount of valid results` / `Total amount of papers`) * 100, 1), "%")) |>
  arrange(`Success rate`) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = F)

# By paper
paper_llm_score_cld |>
  group_by(`Paper ID` = paper_id) |>
  summarize(
    `Total amount of configurations` = n(),
    `Amount of valid results` = sum(is_valid),
    `Amount of failed results`  = sum(is_failed),
    `Amount of skipped results` = sum(is_skipped),
    .groups = "drop"
  ) |>
  mutate(`Success rate` = paste0(round((`Amount of valid results` / `Total amount of configurations`) * 100, 1), "%")) |>
  arrange(`Success rate`) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = F)
```

## Human-authored reviews

The first table shows which paper has been processed other than a single time.
The second table shows for each paper if it yielded a valid result in the identification game or a failed result.
###! Here I feel like I can not summarize the tables but they take much space. Should I drop this information?

```{r}
# Any not processed papers?
paper_human_score_cld |> 
  count(`Paper ID` = paper_id) |> 
  rename(`Amount` = n) |> 
  filter(`Amount` != 1) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

paper_human_score_cld |>
  group_by(`Paper ID` = paper_id) |>
  summarize(
    `Valid result` = sum(is_valid),
    `Failed result`  = sum(is_failed),
    .groups = "drop"
  ) |>
  arrange(`Failed result`, `Valid result`) |>
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Calculations

## Score transformation and calculations

The `total_score` column contains the final TVD-MI metric. The new column `hyperparameter` combines the information for reasoning and non-reasoning models. The performance mean, the absolute distance to this mean and the succcess rates are calculated. For the human dataset, the success rate is by definition set to 1.

```{r}
# 1. Human Data Processing (Baseline)
paper_human_processed <- paper_human_score_cld |> 
  mutate(paper_id = as.factor(paper_id)) |> 
  mutate(across(contains("score"), ~ suppressWarnings(as.numeric(.)))) |> 
  mutate(
    total_score = (tpr_avg_tvd_mi_score - fpr_avg_tvd_mi_score),
    
    # Success rates (Metric 1); Human validity is 100% by definition
    is_valid = 1,
    is_valid_tpr = 1,
    is_valid_fpr = 1,
    
    # Performance means (Metric 2)
    group_mean = if(all(is.na(total_score))) NA_real_ else mean(total_score, na.rm = TRUE),
    tpr_mean   = if(all(is.na(tpr_avg_tvd_mi_score))) NA_real_ else mean(tpr_avg_tvd_mi_score, na.rm = TRUE),
    fpr_mean   = if(all(is.na(fpr_avg_tvd_mi_score))) NA_real_ else mean(fpr_avg_tvd_mi_score, na.rm = TRUE),
    
    # Individual Absolute Deviations
    abs_dev     = abs(total_score - group_mean),
    tpr_abs_dev = abs(tpr_avg_tvd_mi_score - tpr_mean),
    fpr_abs_dev = abs(fpr_avg_tvd_mi_score - fpr_mean),
    
    # Mean Absolute Deviation (Metric 3)
    mad_mean     = if(all(is.na(abs_dev))) NA_real_ else mean(abs_dev, na.rm = TRUE),
    tpr_mad_mean = if(all(is.na(tpr_abs_dev))) NA_real_ else mean(tpr_abs_dev, na.rm = TRUE),
    fpr_mad_mean = if(all(is.na(fpr_abs_dev))) NA_real_ else mean(fpr_abs_dev, na.rm = TRUE)
  ) |> 
  rename_with(~ paste0(., "_human"), .cols = -c(paper_id)) |> 
  mutate(config_label_human = "Human_Global")

# 2. LLM Data Processing (Config-Level)
paper_llm_processed <- paper_llm_score_cld |> 
  mutate(paper_id = as.factor(paper_id)) |> 
  mutate(across(contains("score"), ~ suppressWarnings(as.numeric(.)))) |> 
  mutate(total_score = (tpr_avg_tvd_mi_score - fpr_avg_tvd_mi_score)) |> 
  mutate(
    model = case_match(
      model,
      "gpt-5-mini-2025-08-07" ~ "GPT-5 Mini",
      "gpt-5-nano-2025-08-07" ~ "GPT-5 Nano",
      "gpt-4o-2024-08-06" ~ "GPT-4o",
      "gpt-4o-mini-2024-07-18" ~ "GPT-4o Mini",
      "o4-mini-2025-04-16" ~ "o4 Mini",
      "o3-mini-2025-01-31" ~ "o3 Mini",
      "gpt-3.5-turbo-0125" ~ "GPT-3.5 Turbo",
      "llama-3.3-70b-versatile" ~ "Llama 3.3 (70B)",
      "deepseek-r1-distill-llama-70b" ~ "DeepSeek R1 (Llama 70B)",
      .default = model
    ),
    hyperparameter = case_when(
      !is.na(reasoning_effort) ~ paste0("Re ", reasoning_effort),
      !is.na(temperature) ~ paste0("Tempr ", temperature),
      TRUE ~ "default"
    ),
    chain_of_thought = case_match(
      chain_of_thought,
      "Explain your thought process step by step." ~ "True",
      NA ~ "False",
      .default = chain_of_thought
    ),
    scope = case_match(
      scope,
      "full_text" ~ "Full text",
      "abstract"  ~ "Abstract only",
      .default = scope
    )
  ) |> 
  unite("temp_config_str", all_of(CONFIG_COL), sep = "_", remove = FALSE) |> 
  mutate(
    config_id = as.numeric(factor(temp_config_str, levels = unique(temp_config_str))),
    config_label = paste0("Config_", config_id)
  ) |> 
  dplyr::select(-temp_config_str) |> 
  group_by(config_label) |> 
  mutate(
    # Success rates (Metric 1)
    success_rate     = mean(is_valid, na.rm = TRUE),
    success_rate_tpr = mean(is_valid_tpr, na.rm = TRUE),
    success_rate_fpr = mean(is_valid_fpr, na.rm = TRUE),
    
    # Performance means (Metric 2)
    group_mean = if(all(is.na(total_score))) NA_real_ else mean(total_score, na.rm = TRUE),
    tpr_mean   = if(all(is.na(tpr_avg_tvd_mi_score))) NA_real_ else mean(tpr_avg_tvd_mi_score, na.rm = TRUE),
    fpr_mean   = if(all(is.na(fpr_avg_tvd_mi_score))) NA_real_ else mean(fpr_avg_tvd_mi_score, na.rm = TRUE),
    
    # Individual Absolute Deviations
    abs_dev     = abs(total_score - group_mean),
    tpr_abs_dev = abs(tpr_avg_tvd_mi_score - tpr_mean),
    fpr_abs_dev = abs(fpr_avg_tvd_mi_score - fpr_mean),
    
    # Mean Absolute Deviation (Metric 3)
    mad_mean     = if(all(is.na(abs_dev))) NA_real_ else mean(abs_dev, na.rm = TRUE),
    tpr_mad_mean = if(all(is.na(tpr_abs_dev))) NA_real_ else mean(tpr_abs_dev, na.rm = TRUE),
    fpr_mad_mean = if(all(is.na(fpr_abs_dev))) NA_real_ else mean(fpr_abs_dev, na.rm = TRUE)
  ) |> 
  ungroup() |>
  left_join(paper_human_processed |> 
              dplyr::select(
                paper_id,
                is_valid_human,
                is_valid_tpr_human,
                is_valid_fpr_human,
                total_score_human,
                group_mean_human,
                tpr_mean_human,
                fpr_mean_human,
                mad_mean_human,
                tpr_mad_mean_human,
                fpr_mad_mean_human
              ),
            by = "paper_id"
  )

# 3. Summary table
summary_table <- paper_llm_processed |> 
  group_by(config_id, model, hyperparameter, chain_of_thought, scope) |> 
  summarize(
    
    # Success
    mean_success_rate     = first(success_rate),
    mean_success_rate_tpr = first(success_rate_tpr),
    mean_success_rate_fpr = first(success_rate_fpr),
    
    # Performance (Mean)
    mean_score     = first(group_mean),
    mean_tpr_score = first(tpr_mean),
    mean_fpr_score = first(fpr_mean),
    
    # Stability (MAD)
    mean_mad     = first(mad_mean),
    mean_tpr_mad = first(tpr_mad_mean),
    mean_fpr_mad = first(fpr_mad_mean),
    
    .groups = "drop"
  )
```

## Bootstraping

The bootstrap randomly selects 1000 values with replacing for the given metric and averages across all these values. NAs are ignored in this part. Values at the alpha level / 2 are extracted as lower and upper bounds.

```{r}
# Configuration
num_iterations <- NUM_ITERATIONS
confidence_lvl <- CONFIDENCE_LVL
global_alpha <- (1 - confidence_lvl) / 2

# Helper function
bootstrap_function <- function(df, 
                              group_col,
                              val_col,
                              tpr_val_col, 
                              fpr_val_col,
                              dev_col,
                              tpr_dev_col,
                              fpr_dev_col,
                              is_valid_col,
                              is_tpr_valid_col,
                              is_fpr_valid_col,
                              iterations = num_iterations, 
                              alpha = global_alpha) {
  
  set.seed(42)
  
  boot_distribution <- map_df(1:iterations, function(i) {
    df |> 
      group_by(.data[[group_col]]) |> 
      slice_sample(prop = 1, replace = TRUE) |> 
      summarise(
        # Plot 1: Success
        boot_success     = mean(.data[[is_valid_col]], na.rm = TRUE),
        boot_success_tpr = mean(.data[[is_tpr_valid_col]], na.rm = TRUE),
        boot_success_fpr = mean(.data[[is_fpr_valid_col]], na.rm = TRUE),
        
        # Plot 2: Performance
        boot_mean     = mean(.data[[val_col]], na.rm = TRUE),
        boot_mean_tpr = mean(.data[[tpr_val_col]], na.rm = TRUE),
        boot_mean_fpr = mean(.data[[fpr_val_col]], na.rm = TRUE),
        
        # Plot 3: Stability (MAD)
        boot_mad     = mean(.data[[dev_col]], na.rm = TRUE),
        boot_mad_tpr = mean(.data[[tpr_dev_col]], na.rm = TRUE),
        boot_mad_fpr = mean(.data[[fpr_dev_col]], na.rm = TRUE),
        
        .groups = "drop"
      )
  })
  
  # Calculate Quantiles
  ci_results <- boot_distribution |> 
    group_by(.data[[group_col]]) |> 
    summarise(
      across(starts_with("boot_"), 
             list(lower = ~quantile(.x, alpha, na.rm = TRUE),
                  upper = ~quantile(.x, 1 - alpha, na.rm = TRUE)),
             .names = "{.col}_{.fn}"),
      .groups = "drop"
    )
  
  return(ci_results)
}
```

```{r}
llm_boot_summary <- bootstrap_function(
  df               = paper_llm_processed,
  group_col        = "config_label",
  val_col          = "total_score",
  tpr_val_col      = "tpr_avg_tvd_mi_score",
  fpr_val_col      = "fpr_avg_tvd_mi_score",
  dev_col          = "abs_dev",
  tpr_dev_col      = "tpr_abs_dev",
  fpr_dev_col      = "fpr_abs_dev",
  is_valid_col     = "is_valid",
  is_tpr_valid_col = "is_valid_tpr",
  is_fpr_valid_col = "is_valid_fpr"
)

human_boot_summary <- bootstrap_function(
  df               = paper_human_processed,
  group_col        = "config_label_human",
  val_col          = "total_score_human",
  tpr_val_col      = "tpr_avg_tvd_mi_score_human",
  fpr_val_col      = "fpr_avg_tvd_mi_score_human",
  dev_col          = "abs_dev_human",
  tpr_dev_col      = "tpr_abs_dev_human",
  fpr_dev_col      = "fpr_abs_dev_human",
  is_valid_col     = "is_valid_human",
  is_tpr_valid_col = "is_valid_tpr_human",
  is_fpr_valid_col = "is_valid_fpr_human"
)
```

```{r}
# Join bootstrap results
paper_llm_processed_bind <- paper_llm_processed |> 
  left_join(llm_boot_summary, by = "config_label") |> 
  cross_join(
    human_boot_summary |>
      dplyr::select(-config_label_human) |> 
      rename_with(~ paste0(.x, "_human")))
```

## Plot preparation

For the specification curve plots some the configuration columns are formated.

```{r}
data_plot <- paper_llm_processed_bind |> 
  mutate(
    model = fct_relevel(
      as.factor(model),
      "DeepSeek R1 (Llama 70B)", "Llama 3.3 (70B)", "GPT-3.5 Turbo", "o3 Mini", 
      "o4 Mini", "GPT-4o Mini", "GPT-4o", "GPT-5 Nano", "GPT-5 Mini"
    ),
    hyperparameter = fct_relevel(
      as.factor(hyperparameter),
      "Tempr 1.5", "Tempr 1", "Tempr 0.5", "Tempr 0", "Re high", "Re low"
    ),
    chain_of_thought = fct_relevel(
      as.factor(chain_of_thought),
      "True", "False"
    ),
    scope = fct_relevel(
      as.factor(scope),
      "Full text", "Abstract only"
    )
  ) |> 
  rename(
    `Model` = model,
    `Hyperparameter` = hyperparameter,
    `CoT<br> used` = chain_of_thought,
    `Scope` = scope
  )
```

# Plots

## Functions

### Distribution plot

```{r}
bar_function <- function(dataset, 
                         base_cols, 
                         total_col,
                         clean_labels, 
                         suffix = "", 
                         plot_title = "Distribution of Score Metrics",
                         plot_subtitle = "TPR = True positive rate; FPR = False positive rate; AVG = Average") {
  
  # Combine user-defined components with the specific total score column
  all_target_cols <- c(base_cols, total_col)
  suffixed_cols   <- paste0(all_target_cols, suffix)
  
  # Create labels: User labels for components + Automatic suffix for the total column
  final_labels <- c(
    clean_labels, 
    paste0("Total Score ", ifelse(suffix == "_human", "Human", "LLM"))
  )
  
  # Build the plot
  bar_plot <- dataset |> 
    dplyr::select(all_of(suffixed_cols)) |> 
    tidyr::pivot_longer(
      cols = everything(),
      names_to = "score_type",
      values_to = "score_value"
    ) |> 
    mutate(
      # Map the actual column names (with suffixes) to our clean labels
      score_type = factor(score_type, levels = suffixed_cols, labels = final_labels),
      # Discrete factor for the -1 to 1 scale
      score_value = factor(score_value, levels = seq(-1, 1, 0.125))
    ) |> 
    ggplot(aes(x = score_value)) +
    geom_bar(alpha = 0.8, color = "black", fill = "grey70") + 
    # scale_x_discrete ensures even empty bins are shown to represent the full range
    scale_x_discrete(drop = FALSE, breaks = as.character(seq(-1, 1, 0.5))) +
    facet_wrap(~score_type, scales = "free_x") +
    theme_minimal() +
    labs(
      title = plot_title,
      subtitle = plot_subtitle,
      x = "Score Value",
      y = "Count"
    ) +
    theme(
      legend.position = "none",
      strip.text = element_text(face = "bold"),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank()
    )
  
  return(bar_plot)
}
```

### Specification curve plot

The plot function for a specification curve is taken from [@cumminsThreatAnalyticFlexibility2025]:

```{r}
specification_curve_plot_with_shading <- function(data,
                                                  outcome = "outcome",
                                                  outcome_name = "Outcome",
                                                  plot_title = NULL,
                                                  interval_lower = NULL,
                                                  interval_upper = NULL,
                                                  rank_by = "rank",
                                                  rank_by_outcome = FALSE,
                                                  relative_height_of_upper_plot = 0.70,
                                                  outcome_cutoff = NULL,
                                                  facet_by = NULL,
                                                  facet_ncol = 2,
                                                  shade_lower = NULL,
                                                  shade_upper = NULL,
                                                  shade_fill_by = NULL,
                                                  shade_values = NULL,
                                                  shade_alpha = 0.5,
                                                  shade_fill_constant = "red",
                                                  mutate_plots = NULL) {
  require(dplyr)
  require(tidyr)
  require(ggplot2)
  require(cowplot)
  require(ggtext)
  require(rlang)
  require(grid)
  
  data <- data |>
    rename(outcome = {{outcome}}, rank = {{rank_by}})
  
  if (!is.null(interval_lower))
    data <- data |> rename(interval_lower = {{interval_lower}})
  else
    data$interval_lower <- data$outcome
  if (!is.null(interval_upper))
    data <- data |> rename(interval_upper = {{interval_upper}})
  else
    data$interval_upper <- data$outcome
  
  if (rank_by_outcome)
    data <- data |> arrange(outcome) |> mutate(rank = dplyr::row_number())
  
  keep_num <- c("rank", "outcome", "interval_lower", "interval_upper")
  if (!is.null(shade_lower))
    keep_num <- c(keep_num, as_name(ensym(shade_lower)))
  if (!is.null(shade_upper))
    keep_num <- c(keep_num, as_name(ensym(shade_upper)))
  
  data <- data |> mutate(across(.cols = -all_of(keep_num), .fns = as.factor))
  exclude_cols_base <- keep_num
  
  facet_name <- NULL
  if (!is.null(facet_by)) {
    facet_sym  <- ensym(facet_by)
    facet_name <- as_name(facet_sym)
    if (!facet_name %in% names(data))
      stop("facet_by column not found in data.")
  }
  
  # specify column that controls fill (will be facet)
  if (!is.null(shade_fill_by)) {
    fill_name <- as_name(ensym(shade_fill_by))
  } else {
    fill_name <- facet_name
  }
  if (!is.null(fill_name))
    exclude_cols_base <- c(exclude_cols_base, fill_name)
  
  # resolve global fill levels & colors (so colors are consistent across facets)
  fill_levels <- if (!is.null(fill_name))
    levels(droplevels(as.factor(data[[fill_name]])))
  else
    NULL
  resolved_fill <- NULL
  if (!is.null(fill_levels) && !is.null(shade_values)) {
    if (!is.null(names(shade_values)) &&
        any(nzchar(names(shade_values)))) {
      resolved_fill <- shade_values[fill_levels]
    } else {
      resolved_fill <- rep(shade_values, length.out = length(fill_levels))
      names(resolved_fill) <- fill_levels
    }
  }
  
  build_one <- function(df,
                        title_text = plot_title,
                        show_y_titles = TRUE) {
    
    # REFINEMENT: Ensure rank order for smooth ribbon rendering
    df <- df |> arrange(rank)
    
    p_estimates <- df |>
      mutate(outcome_name = outcome_name) |>
      ggplot(aes(rank, outcome))
    
    # shaded band behind points/intervals
    if (!is.null(shade_lower) && !is.null(shade_upper)) {
      lower_sym <- ensym(shade_lower)
      upper_sym <- ensym(shade_upper)
      
      band <- df |>
        summarise(
          ymin = dplyr::first(!!lower_sym),
          ymax = dplyr::first(!!upper_sym),
          .groups = "drop"
        )
      
      if (!is.null(fill_name) && fill_name %in% names(df)) {
        band$.__fill <- dplyr::first(df[[fill_name]])
        p_estimates <- p_estimates +
          geom_rect(
            data = band,
            aes(
              xmin = -Inf,
              xmax = Inf,
              ymin = ymin,
              ymax = ymax,
              fill = .__fill
            ),
            alpha = shade_alpha,
            inherit.aes = FALSE,
            show.legend = FALSE
          )
        if (!is.null(resolved_fill)) {
          p_estimates <- p_estimates + scale_fill_manual(values = resolved_fill, guide = "none")
        }
      } else {
        p_estimates <- p_estimates +
          geom_rect(
            data = band,
            aes(
              xmin = -Inf,
              xmax = Inf,
              ymin = ymin,
              ymax = ymax
            ),
            fill = shade_fill_constant,
            alpha = shade_alpha,
            inherit.aes = FALSE,
            show.legend = FALSE
          )
      }
      # ensure band is within the y-scale
      p_estimates <- p_estimates + expand_limits(y = c(band$ymin, band$ymax))
    }
    
    # REFINEMENT: Shaded Ribbon CI instead of linerange
    p_estimates <- p_estimates +
      geom_ribbon(aes(ymin = interval_lower, ymax = interval_upper), 
                  fill = "#ADD8E6", alpha = 0.4) +
      geom_point(shape = "circle", size = 2) +
      facet_grid(
        outcome_name ~ .,
        space = "free_y",
        scales = "free_y",
        switch = "y"
      ) +
      scale_y_continuous(breaks = scales::pretty_breaks()) +
      scale_x_continuous(NULL, expand = c(.02, .02)) +
      ylab(if (show_y_titles)
        "Simulation results"
        else
          NULL) +
      theme_minimal() +
      theme(
        legend.position   = "none",
        axis.line.x       = element_blank(),
        strip.placement   = "outside",
        strip.background  = element_rect(fill = NA, colour = NA),
        panel.spacing.x   = unit(0.15, "cm"),
        strip.text.y.left = if (show_y_titles)
          ggtext::element_markdown(
            angle = 90,
            face = "bold",
            size = 7,
            margin = margin(r = 20, l = 5) # REFINEMENT
          )
        else
          element_blank(),
        axis.text.y       = element_text(
          angle = 0,
          hjust = 0.5,
          size = 6
        ),
        axis.title.y      = if (show_y_titles)
          element_text(
            size = 9,
            face = "bold",
            margin = margin(r = 4)
          )
        else
          element_blank(),
        panel.spacing     = unit(0.25, "lines"),
        axis.title.x      = element_blank(),
        axis.text.x       = element_blank(),
        axis.ticks.x      = element_blank()
      )
    
    if (!is.null(outcome_cutoff)) {
      p_estimates <- p_estimates + geom_hline(yintercept = outcome_cutoff, linetype = "dotted")
    }
    
    exclude_cols <- exclude_cols_base
    if (!is.null(facet_name))
      exclude_cols <- c(exclude_cols, facet_name)
    
    p_specs <- df |>
      tidyr::pivot_longer(cols = -dplyr::all_of(exclude_cols)) |>
      arrange(rank) |>
      ggplot(aes(
        x = rank,
        y = factor(value),
        color = name
      )) +
      geom_point(size = 3.5, shape = "|") +
      facet_grid(name ~ .,
                 space = "free_y",
                 scales = "free_y",
                 switch = "y") +
      guides(color = "none") +
      scale_x_continuous(NULL, expand = c(.02, .02)) +
      ylab(if (show_y_titles)
        "Simulation conditions"
        else
          NULL) +
      theme_minimal() +
      theme(
        strip.placement   = "outside",
        strip.background  = element_rect(fill = NA, colour = NA),
        panel.spacing.x   = unit(0.15, "cm"),
        strip.text.y.left = if (show_y_titles)
          ggtext::element_markdown(
            angle = 90,
            face = "bold",
            size = 7,
            # REFINEMENT:
            lineheight = 0.9,
            margin = margin(r = 20, l = 5)
          )
        else
          element_blank(),
        axis.text.y       = element_text(
          angle = 0,
          hjust = 1,
          size = 6
        ),
        axis.title.y      = if (show_y_titles)
          element_text(
            size = 9,
            face = "bold",
            margin = margin(r = 4)
          )
        else
          element_blank(),
        panel.spacing     = unit(0.25, "lines"),
        axis.title.x      = element_blank(),
        axis.text.x       = element_blank(),
        axis.ticks.x      = element_blank()
      ) +
      scale_color_brewer(palette = "Dark2")
    
    if (is.function(mutate_plots)) {
      out <- mutate_plots(p_estimates, p_specs, df)
      if (inherits(out, "gg")) {
        p_estimates <- out
      } else if (is.list(out)) {
        if (length(out) >= 1)
          p_estimates <- out[[1]]
        if (length(out) >= 2)
          p_specs     <- out[[2]]
      }
    }
    
    g_est <- ggplotGrob(p_estimates)
    g_spc <- ggplotGrob(p_specs)
    max_w <- unit.pmax(g_est$widths, g_spc$widths)
    g_est$widths <- max_w
    g_spc$widths <- max_w
    
    combo <- cowplot::plot_grid(
      g_est,
      g_spc,
      axis = "bltr",
      align = "v",
      ncol = 1,
      rel_heights = c(relative_height_of_upper_plot, 1)
    )
    if (!is.null(title_text)) {
      title_grob <- cowplot::ggdraw() +
        cowplot::draw_label(
          title_text,
          x = 0.5,
          hjust = 0.5,
          y = 0.5, # REFINEMENT
          vjust = 0.5, # REFINEMENT
          fontface = "bold"
        )
      combo <- cowplot::plot_grid(title_grob,
                                  combo,
                                  ncol = 1,
                                  rel_heights = c(0.15, 1)) # REFINEMENT
    }
    combo
  }
  
  if (is.null(facet_by))
    return(build_one(data, plot_title, show_y_titles = TRUE))
  
  facet_vals <- if (is.factor(data[[facet_name]]))
    levels(droplevels(data[[facet_name]]))
  else
    unique(data[[facet_name]])
  plotlist <- lapply(seq_along(facet_vals), function(i) {
    v  <- facet_vals[i]
    df <- dplyr::filter(data, .data[[facet_name]] == v)
    if (nrow(df) == 0)
      return(NULL)
    local_title <- if (!is.null(plot_title))
      paste0(plot_title, ": ", v)
    else
      paste0(facet_name, ": ", v)
    is_left_col <- ((i - 1) %% facet_ncol) == 0
    build_one(df, local_title, show_y_titles = is_left_col)
  })
  plotlist <- Filter(Negate(is.null), plotlist)
  
  cowplot::plot_grid(plotlist = plotlist,
                     ncol = facet_ncol,
                     align = "hv")
}
```

## Distribution llm scores

```{r}
paper_llm_scores <- bar_function(
  dataset      = paper_llm_processed,
  base_cols    = BASE_SCORE_COLS,
  total_col    = TOTAL_SCORE_COL,
  clean_labels = CLEAN_SCORE_COLS
)

paper_llm_scores
```

## Distribution human scores

```{r}
paper_human_scores <- bar_function(
  dataset      = paper_human_processed,
  base_cols    = BASE_SCORE_COLS,
  total_col    = TOTAL_SCORE_COL,
  clean_labels = CLEAN_SCORE_COLS,
  suffix = "_human",
)

paper_human_scores
```

## Success rate

```{r}
###! My idea is to place all the tpr/fpr plots beside the main TVD-MI score plots or to put them in the appendix; In case I keep all nine plots, should I wrapp all of this into a function?

success_spec_plot <- data_plot |>  
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    success_rate,
    boot_success_lower,      
    boot_success_upper
  ) |>  
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |>
  summarise(
    success_rate = mean(success_rate),
    boot_success_lower = mean(boot_success_lower),
    boot_success_upper = mean(boot_success_upper),
    .groups = "drop"
  ) |> 
  arrange(success_rate) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
  outcome = success_rate,
  outcome_name = "Success rate TVD-MI",
  plot_title = "Specification Curve: Success rate by Configuration",
  interval_lower = "boot_success_lower",
  interval_upper = "boot_success_upper",
  rank_by = rank,
  
  mutate_plots = \(top, bottom, df) {
    list(top + coord_cartesian(ylim = c(0, 1)))
  }
)
```

```{r}
success_tpr_spec_plot <- data_plot |>  
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    success_rate_tpr,
    boot_success_tpr_lower,      
    boot_success_tpr_upper
  ) |>  
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |>
  summarise(
    success_rate_tpr = mean(success_rate_tpr),
    boot_success_tpr_lower = mean(boot_success_tpr_lower),
    boot_success_tpr_upper = mean(boot_success_tpr_upper),
    .groups = "drop"
  ) |> 
  arrange(success_rate_tpr) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
  outcome = success_rate_tpr,
  outcome_name = "Success rate TPR",
  plot_title = "Specification Curve: Success rate by Configuration",
  interval_lower = "boot_success_tpr_lower",
  interval_upper = "boot_success_tpr_upper",
  rank_by = rank,
  
  mutate_plots = \(top, bottom, df) {
    list(top + coord_cartesian(ylim = c(0, 1)))
  }
)
```


```{r}
success_fpr_spec_plot <- data_plot |>  
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    success_rate_fpr,
    boot_success_fpr_lower,      
    boot_success_fpr_upper
  ) |>  
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |>
  summarise(
    success_rate_fpr = mean(success_rate_fpr),
    boot_success_fpr_lower = mean(boot_success_fpr_lower),
    boot_success_fpr_upper = mean(boot_success_fpr_upper),
    .groups = "drop"
  ) |> 
  arrange(success_rate_fpr) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
  outcome = success_rate_fpr,
  outcome_name = "Success rate FPR",
  plot_title = "Specification Curve: Success rate by Configuration",
  interval_lower = "boot_success_fpr_lower",
  interval_upper = "boot_success_fpr_upper",
  rank_by = rank,
  
  mutate_plots = \(top, bottom, df) {
    list(top + coord_cartesian(ylim = c(0, 1)))
  }
)
```


```{r}
success_spec_plot

success_tpr_spec_plot

success_fpr_spec_plot
```

## Mean

```{r}
###! The quality assessment ignores how many unsuccessful combos a configuration had. Should I include this information, e.g. via the transparency of the data point (alpha) or might this more confusing than helpful?

mean_spec_plot <- data_plot |> 
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    group_mean, 
    boot_mean_lower, 
    boot_mean_upper,
    boot_mean_lower_human, 
    boot_mean_upper_human
  ) |> 
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |> 
  summarize(
    group_mean = mean(group_mean),
    boot_mean_lower = mean(boot_mean_lower),
    boot_mean_upper = mean(boot_mean_upper),
    boot_mean_lower_human = mean(boot_mean_lower_human),
    boot_mean_upper_human = mean(boot_mean_upper_human),
    .groups = "drop"
  ) |> 
  arrange(group_mean) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
    # Basic content
    outcome = group_mean,
    outcome_name = "Mean TVD-MI score",
    plot_title = "Specification Curve: Mean by Configuration",
    interval_lower = "boot_mean_lower",
    interval_upper = "boot_mean_upper",
    rank_by = rank,
    # CI base
    shade_lower = "boot_mean_lower_human",
    shade_upper = "boot_mean_upper_human",
    
    mutate_plots = \(top, bottom, df) {
      list(top + coord_cartesian(ylim = c(-1, 1)))
    }
  )
```

```{r}
mean_spec_tpr_plot <- data_plot |> 
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    tpr_mean, 
    boot_mean_tpr_lower, 
    boot_mean_tpr_upper,
    boot_mean_tpr_lower_human, 
    boot_mean_tpr_upper_human
  ) |> 
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |> 
  summarize(
    tpr_mean = mean(tpr_mean),
    boot_mean_tpr_lower = mean(boot_mean_tpr_lower),
    boot_mean_tpr_upper = mean(boot_mean_tpr_upper),
    boot_mean_tpr_lower_human = mean(boot_mean_tpr_lower_human),
    boot_mean_tpr_upper_human = mean(boot_mean_tpr_upper_human),
    .groups = "drop"
  ) |> 
  arrange(tpr_mean) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
    # Basic content
    outcome = tpr_mean,
    outcome_name = "Mean TPR",
    plot_title = "Specification Curve: Mean by Configuration",
    interval_lower = "boot_mean_tpr_lower",
    interval_upper = "boot_mean_tpr_upper",
    rank_by = rank,
    # CI base
    shade_lower = "boot_mean_tpr_lower_human",
    shade_upper = "boot_mean_tpr_upper_human",
    
    mutate_plots = \(top, bottom, df) {
      list(top + coord_cartesian(ylim = c(-1, 1)))
    }
  )
```

```{r}
mean_spec_fpr_plot <- data_plot |> 
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    fpr_mean, 
    boot_mean_fpr_lower, 
    boot_mean_fpr_upper,
    boot_mean_fpr_lower_human, 
    boot_mean_fpr_upper_human
  ) |> 
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |> 
  summarize(
    fpr_mean = mean(fpr_mean),
    boot_mean_fpr_lower = mean(boot_mean_fpr_lower),
    boot_mean_fpr_upper = mean(boot_mean_fpr_upper),
    boot_mean_fpr_lower_human = mean(boot_mean_fpr_lower_human),
    boot_mean_fpr_upper_human = mean(boot_mean_fpr_upper_human),
    .groups = "drop"
  ) |> 
  arrange(fpr_mean) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
    # Basic content
    outcome = fpr_mean,
    outcome_name = "Mean FPR",
    plot_title = "Specification Curve: Mean by Configuration",
    interval_lower = "boot_mean_fpr_lower",
    interval_upper = "boot_mean_fpr_upper",
    rank_by = rank,
    # CI base
    shade_lower = "boot_mean_fpr_lower_human",
    shade_upper = "boot_mean_fpr_upper_human",
    
    mutate_plots = \(top, bottom, df) {
      list(top + coord_cartesian(ylim = c(-1, 1)))
    }
  )
```

```{r}
mean_spec_plot

mean_spec_tpr_plot

mean_spec_fpr_plot
```

## Distance

```{r}
distance_spec_plot <- data_plot |>  
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    mad_mean, 
    boot_mad_lower, 
    boot_mad_upper,
    boot_mad_lower_human,
    boot_mad_upper_human
  ) |> 
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |> 
  summarize(
    mad_mean = mean(mad_mean),
    boot_mad_lower = mean(boot_mad_lower),
    boot_mad_upper = mean(boot_mad_upper),
    boot_mad_lower_human = mean(boot_mad_lower_human),
    boot_mad_upper_human = mean(boot_mad_upper_human),
    .groups = "drop"
  ) |> 
  arrange(mad_mean) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
    # Basic content
    outcome = mad_mean,
    outcome_name = "Avg. dis. to<br>mean TVD-MI score",
    plot_title = "Specification Curve: Average distance by Configuration",
    interval_lower = "boot_mad_lower",
    interval_upper = "boot_mad_upper",
    rank_by = rank,
    # CI base
    shade_lower = "boot_mad_lower_human",
    shade_upper = "boot_mad_upper_human",
    
    mutate_plots = \(top, bottom, df) {
      list(top + coord_cartesian(ylim = c(-1, 1)))
    }
  )
```

```{r}
distance_tpr_spec_plot <- data_plot |>  
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    tpr_mad_mean, 
    boot_mad_tpr_lower, 
    boot_mad_tpr_upper,
    boot_mad_tpr_lower_human,
    boot_mad_tpr_upper_human
  ) |> 
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |> 
  summarize(
    tpr_mad_mean = mean(tpr_mad_mean),
    boot_mad_tpr_lower = mean(boot_mad_tpr_lower),
    boot_mad_tpr_upper = mean(boot_mad_tpr_upper),
    boot_mad_tpr_lower_human = mean(boot_mad_tpr_lower_human),
    boot_mad_tpr_upper_human = mean(boot_mad_tpr_upper_human),
    .groups = "drop"
  ) |> 
  arrange(tpr_mad_mean) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
    # Basic content
    outcome = tpr_mad_mean,
    outcome_name = "Avg. dis. to mean TPR",
    plot_title = "Specification Curve: Average distance by Configuration",
    interval_lower = "boot_mad_tpr_lower",
    interval_upper = "boot_mad_tpr_upper",
    rank_by = rank,
    # CI base
    shade_lower = "boot_mad_tpr_lower_human",
    shade_upper = "boot_mad_tpr_upper_human",
    
    mutate_plots = \(top, bottom, df) {
      list(top + coord_cartesian(ylim = c(-1, 1)))
    }
  )
```

```{r}
distance_fpr_spec_plot <- data_plot |>  
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyperparameter`, 
    `CoT<br> used`, 
    `Scope`, 
    fpr_mad_mean, 
    boot_mad_fpr_lower, 
    boot_mad_fpr_upper,
    boot_mad_fpr_lower_human,
    boot_mad_fpr_upper_human
  ) |> 
  # Summarize
  group_by(Model, Hyperparameter, `CoT<br> used`, Scope) |> 
  summarize(
    fpr_mad_mean = mean(fpr_mad_mean),
    boot_mad_fpr_lower = mean(boot_mad_fpr_lower),
    boot_mad_fpr_upper = mean(boot_mad_fpr_upper),
    boot_mad_fpr_lower_human = mean(boot_mad_fpr_lower_human),
    boot_mad_fpr_upper_human = mean(boot_mad_fpr_upper_human),
    .groups = "drop"
  ) |> 
  arrange(fpr_mad_mean) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
    # Basic content
    outcome = fpr_mad_mean,
    outcome_name = "Avg. dis. to mean FPR",
    plot_title = "Specification Curve: Average distance by Configuration",
    interval_lower = "boot_mad_fpr_lower",
    interval_upper = "boot_mad_fpr_upper",
    rank_by = rank,
    # CI base
    shade_lower = "boot_mad_fpr_lower_human",
    shade_upper = "boot_mad_fpr_upper_human",
    
    mutate_plots = \(top, bottom, df) {
      list(top + coord_cartesian(ylim = c(-1, 1)))
    }
  )
```

```{r}
distance_spec_plot

distance_tpr_spec_plot

distance_fpr_spec_plot
```

# Inferential tests

```{r}
# Function for conditional posthoc tests
conditional_posthoc_function <- function(model, alpha = 0.05, adjust = "bonferroni") {
  
  # Check if model is binomial (glmer) or linear (lmer)
  is_glmer <- inherits(model, "glmerMod")
  test_stat <- if(is_glmer) "Chisq" else "F"
  
  anova_res <- tryCatch({
    car::Anova(model, type = "II", test.statistic = test_stat)
  }, error = function(e) {
    message("ANOVA failed: ", e$message)
    return(NULL)
  })
  
  if(is.null(anova_res)) return(NULL)
  
  # Identify the p-value column (it's either Pr(>Chisq) or Pr(>F))
  p_col <- grep("Pr\\(>", colnames(anova_res), value = TRUE)
  
  # Handle cases where no terms are significant
  sig_mask <- anova_res[[p_col]] < alpha
  terms <- rownames(anova_res)[sig_mask]
  terms <- terms[!terms %in% c("(Intercept)", "Residuals")]
  
  if(length(terms) == 0) {
    message("No significant terms found at alpha ", alpha)
    return(list(anova = anova_res, posthoc = list()))
  }
  
  # Run post-hoc tests
  results <- lapply(terms, function(term) {

    spec_formula <- as.formula(paste("~", term))
    
    # Calculate Estimated Marginal Means
    emm <- emmeans::emmeans(model, specs = spec_formula, type = "response")
    
    # Compact Letter Display (CLD)
    multcomp::cld(emm, 
                  alpha = alpha, 
                  Letters = c(letters, LETTERS), 
                  adjust = adjust, 
                  reversed = TRUE) |> 
      as.data.frame() |> 
      mutate(term = term)
  })
  
  names(results) <- terms
  return(list(anova = anova_res, posthoc = results))
}
```

## Success rates

```{r}
# 1. Total TVD-MI Success
glmer_success_total <- lme4::glmer(is_valid ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                                   data = paper_llm_processed, family = binomial)
posthoc_success_total <- conditional_posthoc_function(glmer_success_total, alpha = ALPHA, adjust = POST_HOC_CORRECTION)

# 2. TPR Success
glmer_success_tpr <- lme4::glmer(is_valid_tpr ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                                 data = paper_llm_processed, family = binomial)
posthoc_success_tpr <- conditional_posthoc_function(glmer_success_tpr, alpha = ALPHA, adjust = POST_HOC_CORRECTION)

# 3. FPR Success
glmer_success_fpr <- lme4::glmer(is_valid_fpr ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                                 data = paper_llm_processed, family = binomial)
posthoc_success_fpr <- conditional_posthoc_function(glmer_success_fpr, alpha = ALPHA, adjust = POST_HOC_CORRECTION)
```

```{r}
posthoc_success_total

posthoc_success_tpr

posthoc_success_fpr
```


## Mean performance

```{r}
###! By default the function deletes any combo which includes NAs. This can lead to bias, benefitial for combos with a small amount of kept rows, as my data is not missing at random. Can I still run them like this?

# 4. Total Score Mean
lmm_mean_total <- lme4::lmer(total_score ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                             data = paper_llm_processed)
posthoc_mean_total <- conditional_posthoc_function(lmm_mean_total, alpha = ALPHA, adjust = POST_HOC_CORRECTION)

# 5. TPR Score Mean
lmm_mean_tpr <- lme4::lmer(tpr_avg_tvd_mi_score ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                           data = paper_llm_processed)
posthoc_mean_tpr <- conditional_posthoc_function(lmm_mean_tpr, alpha = ALPHA, adjust = POST_HOC_CORRECTION)

# 6. FPR Score Mean
lmm_mean_fpr <- lme4::lmer(fpr_avg_tvd_mi_score ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                           data = paper_llm_processed)
posthoc_mean_fpr <- conditional_posthoc_function(lmm_mean_fpr, alpha = ALPHA, adjust = POST_HOC_CORRECTION)
```

```{r}
posthoc_mean_total

posthoc_mean_tpr

posthoc_mean_fpr
```


## Stability (Mean Absolute Deviation)

```{r}
# 7. Total Score Stability (MAD)
lmm_mad_total <- lme4::lmer(abs_dev ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                            data = paper_llm_processed)
posthoc_mad_total <- conditional_posthoc_function(lmm_mad_total, alpha = ALPHA, adjust = POST_HOC_CORRECTION)

# 8. TPR Stability (MAD)
lmm_mad_tpr <- lme4::lmer(tpr_abs_dev ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                          data = paper_llm_processed)
posthoc_mad_tpr <- conditional_posthoc_function(lmm_mad_tpr, alpha = ALPHA, adjust = POST_HOC_CORRECTION)

# 9. FPR Stability (MAD)
lmm_mad_fpr <- lme4::lmer(fpr_abs_dev ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                          data = paper_llm_processed)
posthoc_mad_fpr <- conditional_posthoc_function(lmm_mad_fpr, alpha = ALPHA, adjust = POST_HOC_CORRECTION)
```

```{r}
posthoc_mad_total

posthoc_mad_tpr

posthoc_mad_fpr
```


# Session info

```{r}
sessionInfo()
```

# References

::: {#refs}
:::
