---
title: "Analyses"
author: "Lars Schilling"
date: last-modified
date-format: "YYYY-MM-DD HH:mm:ss"
bibliography: references.bib
csl: apa.csl
editor: visual
format:
  html:
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    highlight-style: haddock
    theme: flatly
    toc: true
    toc-location: left
    embed-resources: true
execute:
  warning: false
  message: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
```

# Dependencies

```{r}
working_dir <- "G:/Meine Ablage/Analytic_flexbility_llm_reviews/simulated_data/tvd_mi"

paper_llm_score_name <- "tvd_mi_scores_paper_llm_review_1.parquet"

paper_human_name <- "tvd_mi_scores_paper_human_review_2.parquet"
```

```{r}
# Flags for skipped or invalid API responses
SKIP_MESSAGE <- "Skipped cause of invalid input"
TOTAL_FAILURE_MESSAGE = "LLM call failed after multiple retries"

AMOUNT_SETTINGS <- 112 # Set to expected amount of configuration setting
AMOUNT_PAPERS <- 98 # Set to expected amount of parsed papers

COMBO_COL <- c("paper_id", "model", "temperature", "reasoning_effort", "chain_of_thought", "scope") # Set to expected combo columns
CONFIG_COL <- c("model", "hyperparameter", "chain_of_thought", "scope") # Set to expected configuration columns
BASE_SCORE_COLS <- c(
  "tpr_tvd_mi_score_1", "tpr_tvd_mi_score_2", "tpr_avg_tvd_mi_score",
  "fpr_tvd_mi_score_1", "fpr_tvd_mi_score_2", "fpr_avg_tvd_mi_score"
) # Set to expected score columns
CLEAN_SCORE_COLS <- c(
  "TPR 1", "TPR 2", "TPR AVG", 
  "FPR 1", "FPR 2", "FPR AVG"
) # Set to wanted score labels
TOTAL_SCORE_COL <- "tvd_mi_score" # Set to created total score column

# Bootstrap settings
NUM_ITERATIONS <- 1000
CONFIDENCE_LVL <- 0.95

# Posthoc-test settings
###! Holmes-correction was not possible. Should I switch to bonferroni, Tuckey or try another way to run post-hoc tests?
ALPHA <- 0.05
POST_HOC_CORRECTION = "bonferroni"
```

```{r, results= 'hide'}
load_pkg <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}

load_pkg("arrow")
load_pkg("tidyverse")
load_pkg("lme4")
load_pkg("car")
load_pkg("emmeans")
load_pkg("multcomp")
load_pkg("multcompView")
load_pkg("broom.mixed")
load_pkg("transport")
load_pkg("knitr")
load_pkg("kableExtra")
load_pkg("cowplot")
load_pkg("ggtext")
```

# Load data

```{r}
full_path_paper_llm <- file.path(working_dir, paper_llm_score_name)


paper_llm_score <- read_parquet(full_path_paper_llm,
                                as_data_frame = TRUE, mmap = TRUE)

full_path_paper_human <- file.path(working_dir, paper_human_name)

paper_human_score <- read_parquet(full_path_paper_human,
                                  as_data_frame = TRUE, mmap = TRUE)
```

# Content checks

As multiple runs of APIs possibly created duplicate paper/configuration pairs, these have to be cleaned first. Besides that, the function creates metadata-columns which indicate weather combinations of paper and configuration have been attempted, and weather they yielded valid TPRs and FPRs in that case.

```{r}
# Helper function to clean duplicates with granular success flags
clean_duplicates_function <- function(df, 
                                      combo_cols, 
                                      tpr_col, 
                                      fpr_col, 
                                      skip_msg = SKIP_MESSAGE, 
                                      fail_msg = TOTAL_FAILURE_MESSAGE) {
  
  df_cleaned <- df |>
    mutate(
      # Individual validity for the sub-metrics
      is_valid_tpr = !(.data[[tpr_col]] %in% c(skip_msg, fail_msg)),
      is_valid_fpr = !(.data[[fpr_col]] %in% c(skip_msg, fail_msg)),
      
      # The TVD-MI is only valid if BOTH are valid (Success of the TVD-MI score)
      is_valid = is_valid_tpr & is_valid_fpr,
      
      # Fail and skip flags for the compelete tier list
      is_failed  = (.data[[tpr_col]] %in% fail_msg | .data[[fpr_col]] %in% fail_msg),
      is_skipped = (.data[[tpr_col]] %in% skip_msg & .data[[fpr_col]] %in% skip_msg),
    ) |>
    mutate(
      quality_tier = case_when(
        is_valid   ~ 1, # Both TPR and FPR are clean
        is_failed  ~ 2, # Judge error
        is_skipped ~ 3, # Review generation error
        TRUE       ~ 4
      ),
      .orig_idx = row_number()
    ) |>
    group_by(pick(all_of(combo_cols))) |>
    arrange(quality_tier, .orig_idx, .by_group = TRUE) |>
    slice(1) |>
    ungroup() |>
    dplyr::select(-any_of(c(".orig_idx")))
  
  return(df_cleaned)
}
```

```{r}
paper_llm_score_cld <- clean_duplicates_function(paper_llm_score,
                                                 COMBO_COL,
                                                 "tpr_avg_tvd_mi_score",
                                                 "fpr_avg_tvd_mi_score")

paper_human_score_cld <- clean_duplicates_function(paper_human_score,
                                                  "paper_id",
                                                  "tpr_avg_tvd_mi_score",
                                                  "fpr_avg_tvd_mi_score")
```

# Completness checks

Incomplete or frequently skipped/invalid combinations papers, configurations and combinations are not dropped, but in case the following indicates odd results these will be taken into consideration in the result interpretation. ###! Is it OK to do that or should I also define a exclusion criteria when I write such code?

## LLM-authored reviews

### Any incomplete processed papers?

```{r}
paper_llm_score_cld |> 
  count(`Paper ID` = paper_id) |> 
  filter(n != AMOUNT_SETTINGS) |> 
  rename(`Amount of processed configurations` = n) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) |> 
  scroll_box(width = "100%", height = "400px")
```

### Any incompletely proccessed configurations?

```{r}
paper_llm_score_cld |> 
  group_by(Model = model, Temperature = temperature, `Reasoning effort` = reasoning_effort,
           CoT = chain_of_thought, `Scope` = scope, ) |> 
  summarize(row_count = n(),
            .groups = "drop") |> 
  filter(row_count != AMOUNT_PAPERS) |>
  rename(`Amount of processed papers` = row_count) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) |> 
  scroll_box(width = "100%", height = "400px")
```

### Status summary global:

```{r}
# Global
paper_llm_score_cld |>
  summarize(
    `Total amount of combinations` = n(),
    `Amount of valid results` = sum(is_valid),
    `Amount of failed results`  = sum(is_failed),
    `Amount of skipped results` = sum(is_skipped),
    .groups = "drop"
  ) |>
  mutate(`Success rate`= paste0(round((`Amount of valid results` / `Total amount of combinations`) * 100, 1), "%")) |>
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F) 
```

### Status Summary by configuration:

```{r}
paper_llm_score_cld |>
  group_by(model, temperature, reasoning_effort, chain_of_thought, scope) |>
  summarize(
    `Total amount of papers` = n(),
    `Amount of valid results` = sum(is_valid),
    `Amount of failed results`  = sum(is_failed),
    `Amount of skipped results` = sum(is_skipped),
    .groups = "drop"
  ) |>
  mutate(`Success rate` = paste0(round((`Amount of valid results` / `Total amount of papers`) * 100, 1), "%")) |>
  arrange(`Success rate`) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = F) |> 
  scroll_box(width = "100%", height = "400px")
```

### Status summary by paper:

```{r}
paper_llm_score_cld |>
  group_by(`Paper ID` = paper_id) |>
  summarize(
    `Total amount of configurations` = n(),
    `Amount of valid results` = sum(is_valid),
    `Amount of failed results`  = sum(is_failed),
    `Amount of skipped results` = sum(is_skipped),
    .groups = "drop"
  ) |>
  mutate(`Success rate` = paste0(round((`Amount of valid results` / `Total amount of configurations`) * 100, 1), "%")) |>
  arrange(`Success rate`) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = F) |> 
  scroll_box(width = "100%", height = "400px")
```

## Human-authored reviews

### Any not processed papers?

```{r}
paper_human_score_cld |> 
  count(`Paper ID` = paper_id) |> 
  rename(`Amount` = n) |> 
  filter(`Amount` != 1) |> 
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) |> 
  scroll_box(width = "100%", height = "400px")
```

### Status summary by paper:

```{r}
paper_human_score_cld |>
  group_by(`Paper ID` = paper_id) |>
  summarize(
    `Valid result` = sum(is_valid),
    `Failed result`  = sum(is_failed),
    .groups = "drop"
  ) |>
  arrange(`Failed result`, `Valid result`) |>
  kable(format = "html", align = "r") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) |> 
  scroll_box(width = "100%", height = "400px")
```

# Calculations

## Score transformation and calculations

The `total_score` column contains the final TVD-MI metric. The new column `hyperparameter` combines the information for temperature parameter or reasoning effort parameter. The mean success rate and the mean TVD-MI per configuration group are calculated. For the human data, the success rate is by definition set to 1.

```{r}
# 1. Human Data Processing (Baseline)
paper_human_processed <- paper_human_score_cld |> 
  mutate(paper_id = as.factor(paper_id)) |> 
  mutate(across(contains("score"), ~ suppressWarnings(as.numeric(.)))) |> 
  mutate(
    tvd_mi_score = (tpr_avg_tvd_mi_score - fpr_avg_tvd_mi_score),
    
    # Success rates (Metric 1); Human validity is 100% by definition
    success_rate = 1,
    
    # Performance means (Metric 2 and 3)
    group_mean = if(all(is.na(tvd_mi_score))) NA_real_ else mean(tvd_mi_score, na.rm = TRUE),

  ) |> 
  rename_with(~ paste0(., "_human"), .cols = -c(paper_id)) |> 
  mutate(config_label_human = "Human_Global")

# 2. LLM Data Processing (Config-Level)
paper_llm_processed <- paper_llm_score_cld |> 
  mutate(paper_id = as.factor(paper_id)) |> 
  mutate(across(contains("score"), ~ suppressWarnings(as.numeric(.)))) |> 
  mutate(
    model = case_match(
      model,
      "gpt-5-mini-2025-08-07" ~ "GPT-5 Mini",
      "gpt-5-nano-2025-08-07" ~ "GPT-5 Nano",
      "gpt-4o-2024-08-06" ~ "GPT-4o",
      "gpt-4o-mini-2024-07-18" ~ "GPT-4o Mini",
      "o4-mini-2025-04-16" ~ "o4 Mini",
      "o3-mini-2025-01-31" ~ "o3 Mini",
      "gpt-3.5-turbo-0125" ~ "GPT-3.5 Turbo",
      "llama-3.3-70b-versatile" ~ "Llama 3.3 (70B)",
      "deepseek-r1-distill-llama-70b" ~ "DeepSeek R1 (Llama 70B)",
      .default = model
    ),
    hyperparameter = case_when(
      !is.na(reasoning_effort) ~ paste0("Re ", reasoning_effort),
      !is.na(temperature) ~ paste0("Tempr ", temperature),
      TRUE ~ "default"
    ),
    chain_of_thought = case_match(
      chain_of_thought,
      "Explain your thought process step by step." ~ "True",
      NA ~ "False",
      .default = chain_of_thought
    ),
    scope = case_match(
      scope,
      "full_text" ~ "Full text",
      "abstract"  ~ "Abstract only",
      .default = scope
    )
  ) |> 
  mutate(
    tvd_mi_score = (tpr_avg_tvd_mi_score - fpr_avg_tvd_mi_score),
    is_created = (1 - is_skipped)
    ) |> 
  unite("temp_config_str", all_of(CONFIG_COL), sep = "_", remove = FALSE) |> 
  mutate(
    config_id = as.numeric(factor(temp_config_str, levels = unique(temp_config_str))),
    config_label = paste0("Config_", config_id)
  ) |> 
  dplyr::select(-temp_config_str) |> 
  group_by(config_label) |> 
  mutate(
    # Success rates (Metric 1)
    success_rate     = mean(is_created, na.rm = TRUE),

    # Performance means (Metric 2)
    group_mean = if(all(is.na(tvd_mi_score))) NA_real_ else mean(tvd_mi_score, na.rm = TRUE),
  ) |> 
  ungroup() |>
  left_join(paper_human_processed |> 
              dplyr::select(
                paper_id,
                success_rate_human,
                tvd_mi_score_human,
                group_mean_human
              ),
            by = "paper_id"
  )

# 3. Summary table
summary_table <- paper_llm_processed |> 
  group_by(config_id) |> 
  summarize(
    
    # Success
    mean_success_rate     = first(success_rate),
    
    # Performance (Mean)
    mean_score     = first(group_mean),
    
    .groups = "drop"
  )
```

## Bootstraping

The bootstrap randomly selects 1000 values with replacing for the given metric and averages across all these values. This process is done for each configuration group. Total scores are ignored. Values at the alpha level / 2 are extracted as lower and upper bounds.

```{r}
# Configuration
num_iterations <- NUM_ITERATIONS
confidence_lvl <- CONFIDENCE_LVL
global_alpha <- (1 - confidence_lvl) / 2

# Helper function
bootstrap_function <- function(df, 
                              group_col,
                              score_col,
                              is_created_col = NULL, # Optional
                              iterations = num_iterations, 
                              alpha = global_alpha,
                              calc_success = FALSE) {
  
  set.seed(42)
  
  boot_distribution <- map_df(1:iterations, function(i) {
    df |> 
      group_by(.data[[group_col]]) |> 
      slice_sample(prop = 1, replace = TRUE) |> 
      summarise(
        # Plot 1: Success
        boot_success = if (calc_success) {
          mean(.data[[is_created_col]], na.rm = TRUE)
        } else {
          NA_real_
        },
        
        # Plot 2: Performance
        boot_mean = mean(.data[[score_col]], na.rm = TRUE),
        
        .groups = "drop"
      )
  })
  
  # Calculate quantiles
  ci_results <- boot_distribution |> 
    group_by(.data[[group_col]]) |> 
    summarise(
      across(starts_with("boot_"), 
             list(lower = ~quantile(.x, alpha, na.rm = TRUE),
                  upper = ~quantile(.x, 1 - alpha, na.rm = TRUE)),
             .names = "{.col}_{.fn}"),
      .groups = "drop"
    )
  
  # Delete empty columns
  if (!calc_success) {
    ci_results <- ci_results |> dplyr::select(-starts_with("boot_success"))
  }
  
  return(ci_results)
}
```

```{r}
llm_boot_summary <- bootstrap_function(
  df = paper_llm_processed,
  group_col = "config_label",
  score_col = "tvd_mi_score",
  is_created_col = "is_created",
  calc_success = TRUE
)

human_boot_summary <- bootstrap_function(
  df = paper_human_processed,
  group_col = "config_label_human",
  score_col = "tvd_mi_score_human",
)
```

```{r}
paper_llm_processed_bind <- paper_llm_processed |> 
  left_join(llm_boot_summary, by = "config_label") |> 
  cross_join(
    human_boot_summary |>
      dplyr::select(-config_label_human) |> 
      rename_with(~ paste0(.x, "_human")))
```

## Plot preparation

For the specification curve plots some the configuration columns are formated.

```{r}
data_plot <- paper_llm_processed_bind |> 
  mutate(
    model = fct_relevel(
      as.factor(model),
      "DeepSeek R1 (Llama 70B)", "Llama 3.3 (70B)", "GPT-3.5 Turbo", "o3 Mini", 
      "o4 Mini", "GPT-4o Mini", "GPT-4o", "GPT-5 Nano", "GPT-5 Mini"
    ),
    hyperparameter = fct_relevel(
      as.factor(hyperparameter),
      "Tempr 1.5", "Tempr 1", "Tempr 0.5", "Tempr 0", "Re high", "Re low"
    ),
    chain_of_thought = fct_relevel(
      as.factor(chain_of_thought),
      "True", "False"
    ),
    scope = fct_relevel(
      as.factor(scope),
      "Full text", "Abstract only"
    )
  ) |> 
  rename(
    `Model` = model,
    `Hyper-<br> parameter` = hyperparameter,
    `CoT<br> used` = chain_of_thought,
    `Scope` = scope
  )
```

# Plots

## Functions

### Distribution plot

```{r}
bar_function <- function(dataset, 
                         base_cols, 
                         total_col,
                         clean_labels, 
                         suffix = "", 
                         plot_title = "Distribution of Score Metrics",
                         plot_subtitle = "TPR = True positive rate; FPR = False positive rate; AVG = Average") {
  
  # Combine user-defined components with the specific total score column
  all_target_cols <- c(base_cols, total_col)
  suffixed_cols   <- paste0(all_target_cols, suffix)
  
  # Create labels: User labels for components + Automatic suffix for the total column
  final_labels <- c(
    clean_labels, 
    paste0("Total Score ", ifelse(suffix == "_human", "Human", "LLM"))
  )
  
  # Build the plot
  bar_plot <- dataset |> 
    dplyr::select(all_of(suffixed_cols)) |> 
    tidyr::pivot_longer(
      cols = everything(),
      names_to = "score_type",
      values_to = "score_value"
    ) |> 
    mutate(
      # Map the actual column names (with suffixes) to our clean labels
      score_type = factor(score_type, levels = suffixed_cols, labels = final_labels),
      # Discrete factor for the -1 to 1 scale
      score_value = factor(score_value, levels = seq(-1, 1, 0.125))
    ) |> 
    ggplot(aes(x = score_value)) +
    geom_bar(alpha = 0.8, color = "black", fill = "grey70") + 
    # scale_x_discrete ensures even empty bins are shown to represent the full range
    scale_x_discrete(drop = FALSE, breaks = as.character(seq(-1, 1, 0.5))) +
    facet_wrap(~score_type, scales = "free_x") +
    theme_minimal() +
    labs(
      title = plot_title,
      subtitle = plot_subtitle,
      x = "Score Value",
      y = "Count"
    ) +
    theme(
      legend.position = "none",
      strip.text = element_text(face = "bold"),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank()
    )
  
  return(bar_plot)
}
```

### Specification curve plot

The plot function for a specification curve is taken from [@cumminsThreatAnalyticFlexibility2025]:

```{r}
specification_curve_plot_with_shading <- function(data,
                                                  outcome = "outcome",
                                                  outcome_name = "Outcome",
                                                  is_processed = NULL,
                                                  plot_title = NULL,
                                                  interval_lower = NULL,
                                                  interval_upper = NULL,
                                                  rank_by = "rank",
                                                  rank_by_outcome = FALSE,
                                                  relative_height_of_upper_plot = 0.70,
                                                  outcome_cutoff = NULL,
                                                  facet_by = NULL,
                                                  facet_ncol = 2,
                                                  shade_lower = NULL,
                                                  shade_upper = NULL,
                                                  shade_fill_by = NULL,
                                                  shade_values = NULL,
                                                  shade_alpha = 0.5,
                                                  shade_fill_constant = "red",
                                                  mutate_plots = NULL) {
  require(dplyr)
  require(tidyr)
  require(ggplot2)
  require(cowplot)
  require(ggtext)
  require(rlang)
  require(grid)
  
  data <- data |>
    rename(outcome = {{outcome}}, rank = {{rank_by}})
  
  # REFINEMENT
  if (rlang::quo_is_null(rlang::enquo(is_processed)) || rlang::quo_is_missing(rlang::enquo(is_processed))) {
    data <- data |> mutate(is_processed = 1.0)
  } else {
    data <- data |> mutate(is_processed = {{is_processed}})
  }
  
  if (!is.null(interval_lower))
    data <- data |> rename(interval_lower = {{interval_lower}})
  else
    data$interval_lower <- data$outcome
  if (!is.null(interval_upper))
    data <- data |> rename(interval_upper = {{interval_upper}})
  else
    data$interval_upper <- data$outcome
  
  if (rank_by_outcome)
    data <- data |> arrange(outcome) |> mutate(rank = dplyr::row_number())
  
  keep_num <- c("rank", "outcome", "interval_lower", "interval_upper", "is_processed")
  if (!is.null(shade_lower))
    keep_num <- c(keep_num, as_name(ensym(shade_lower)))
  if (!is.null(shade_upper))
    keep_num <- c(keep_num, as_name(ensym(shade_upper)))
  
  data <- data |> mutate(across(.cols = -all_of(keep_num), .fns = as.factor))
  exclude_cols_base <- keep_num
  
  facet_name <- NULL
  if (!is.null(facet_by)) {
    facet_sym  <- ensym(facet_by)
    facet_name <- as_name(facet_sym)
    if (!facet_name %in% names(data))
      stop("facet_by column not found in data.")
  }
  
  # specify column that controls fill (will be facet)
  if (!is.null(shade_fill_by)) {
    fill_name <- as_name(ensym(shade_fill_by))
  } else {
    fill_name <- facet_name
  }
  if (!is.null(fill_name))
    exclude_cols_base <- c(exclude_cols_base, fill_name)
  
  # resolve global fill levels & colors (so colors are consistent across facets)
  fill_levels <- if (!is.null(fill_name))
    levels(droplevels(as.factor(data[[fill_name]])))
  else
    NULL
  resolved_fill <- NULL
  if (!is.null(fill_levels) && !is.null(shade_values)) {
    if (!is.null(names(shade_values)) &&
        any(nzchar(names(shade_values)))) {
      resolved_fill <- shade_values[fill_levels]
    } else {
      resolved_fill <- rep(shade_values, length.out = length(fill_levels))
      names(resolved_fill) <- fill_levels
    }
  }
  
  build_one <- function(df,
                        title_text = plot_title,
                        show_y_titles = TRUE) {
    
    # REFINEMENT: Ensure rank order for smooth ribbon rendering
    df <- df |> arrange(rank)
    
    p_estimates <- df |>
      mutate(outcome_name = outcome_name) |>
      ggplot(aes(rank, outcome))
    
    # shaded band behind points/intervals
    if (!is.null(shade_lower) && !is.null(shade_upper)) {
      lower_sym <- ensym(shade_lower)
      upper_sym <- ensym(shade_upper)
      
      band <- df |>
        summarise(
          ymin = dplyr::first(!!lower_sym),
          ymax = dplyr::first(!!upper_sym),
          .groups = "drop"
        )
      
      if (!is.null(fill_name) && fill_name %in% names(df)) {
        band$.__fill <- dplyr::first(df[[fill_name]])
        p_estimates <- p_estimates +
          geom_rect(
            data = band,
            aes(
              xmin = -Inf,
              xmax = Inf,
              ymin = ymin,
              ymax = ymax,
              fill = .__fill
            ),
            alpha = shade_alpha,
            inherit.aes = FALSE,
            show.legend = FALSE
          )
        if (!is.null(resolved_fill)) {
          p_estimates <- p_estimates + scale_fill_manual(values = resolved_fill, guide = "none")
        }
      } else {
        p_estimates <- p_estimates +
          geom_rect(
            data = band,
            aes(
              xmin = -Inf,
              xmax = Inf,
              ymin = ymin,
              ymax = ymax
            ),
            fill = shade_fill_constant,
            alpha = shade_alpha,
            inherit.aes = FALSE,
            show.legend = FALSE
          )
      }
      # ensure band is within the y-scale
      p_estimates <- p_estimates + expand_limits(y = c(band$ymin, band$ymax))
    }
    
    # REFINEMENT: Shaded Ribbon CI instead of linerange
    p_estimates <- p_estimates +
      geom_ribbon(aes(ymin = interval_lower, ymax = interval_upper), 
                  fill = "#ADD8E6", alpha = 0.4) +
      geom_point(aes(alpha = is_processed), shape = "circle", size = 2) + # REFINEMENT
      scale_alpha_continuous(range = c(0.4, 1.0), guide = "none") +
      facet_grid(
        outcome_name ~ .,
        space = "free_y",
        scales = "free_y",
        switch = "y"
      ) +
      scale_y_continuous(breaks = scales::pretty_breaks()) +
      scale_x_continuous(NULL, expand = c(.02, .02)) +
      ylab(if (show_y_titles)
        "Simulation results"
        else
          NULL) +
      theme_minimal() +
      theme(
        legend.position   = "none",
        axis.line.x       = element_blank(),
        strip.placement   = "outside",
        strip.background  = element_rect(fill = NA, colour = NA),
        panel.spacing.x   = unit(0.15, "cm"),
        strip.text.y.left = if (show_y_titles)
          ggtext::element_markdown(
            angle = 90,
            face = "bold",
            size = 7,
            margin = margin(r = 20, l = 5) # REFINEMENT
          )
        else
          element_blank(),
        axis.text.y       = element_text(
          angle = 0,
          hjust = 0.5,
          size = 6
        ),
        axis.title.y      = if (show_y_titles)
          element_text(
            size = 9,
            face = "bold",
            margin = margin(r = 4)
          )
        else
          element_blank(),
        panel.spacing     = unit(0.25, "lines"),
        axis.title.x      = element_blank(),
        axis.text.x       = element_blank(),
        axis.ticks.x      = element_blank()
      )
    
    if (!is.null(outcome_cutoff)) {
      p_estimates <- p_estimates + geom_hline(yintercept = outcome_cutoff, linetype = "dashed") # REFINEMENT
    }
    
    exclude_cols <- exclude_cols_base
    if (!is.null(facet_name))
      exclude_cols <- c(exclude_cols, facet_name)
    
    p_specs <- df |>
      tidyr::pivot_longer(cols = -dplyr::all_of(exclude_cols)) |>
      arrange(rank) |>
      ggplot(aes(
        x = rank,
        y = factor(value),
        color = name
      )) +
      geom_point(size = 3.5, shape = "|") +
      facet_grid(name ~ .,
                 space = "free_y",
                 scales = "free_y",
                 switch = "y") +
      guides(color = "none") +
      scale_x_continuous(NULL, expand = c(.02, .02)) +
      ylab(if (show_y_titles)
        "Simulation conditions"
        else
          NULL) +
      theme_minimal() +
      theme(
        strip.placement   = "outside",
        strip.background  = element_rect(fill = NA, colour = NA),
        panel.spacing.x   = unit(0.15, "cm"),
        strip.text.y.left = if (show_y_titles)
          ggtext::element_markdown(
            angle = 90,
            face = "bold",
            size = 7,
            # REFINEMENT:
            lineheight = 0.9,
            margin = margin(r = 20, l = 5)
          )
        else
          element_blank(),
        axis.text.y       = element_text(
          angle = 0,
          hjust = 1,
          size = 6
        ),
        axis.title.y      = if (show_y_titles)
          element_text(
            size = 9,
            face = "bold",
            margin = margin(r = 4)
          )
        else
          element_blank(),
        panel.spacing     = unit(0.25, "lines"),
        axis.title.x      = element_blank(),
        axis.text.x       = element_blank(),
        axis.ticks.x      = element_blank()
      ) +
      scale_color_brewer(palette = "Dark2")
    
    if (is.function(mutate_plots)) {
      out <- mutate_plots(p_estimates, p_specs, df)
      if (inherits(out, "gg")) {
        p_estimates <- out
      } else if (is.list(out)) {
        if (length(out) >= 1)
          p_estimates <- out[[1]]
        if (length(out) >= 2)
          p_specs     <- out[[2]]
      }
    }
    
    g_est <- ggplotGrob(p_estimates)
    g_spc <- ggplotGrob(p_specs)
    max_w <- unit.pmax(g_est$widths, g_spc$widths)
    g_est$widths <- max_w
    g_spc$widths <- max_w
    
    combo <- cowplot::plot_grid(
      g_est,
      g_spc,
      axis = "bltr",
      align = "v",
      ncol = 1,
      rel_heights = c(relative_height_of_upper_plot, 1)
    )
    if (!is.null(title_text)) {
      title_grob <- cowplot::ggdraw() +
        cowplot::draw_label(
          title_text,
          x = 0.5,
          hjust = 0.5,
          y = 0.5, # REFINEMENT
          vjust = 0.5, # REFINEMENT
          fontface = "bold"
        )
      combo <- cowplot::plot_grid(title_grob,
                                  combo,
                                  ncol = 1,
                                  rel_heights = c(0.15, 1)) # REFINEMENT
    }
    combo
  }
  
  if (is.null(facet_by))
    return(build_one(data, plot_title, show_y_titles = TRUE))
  
  facet_vals <- if (is.factor(data[[facet_name]]))
    levels(droplevels(data[[facet_name]]))
  else
    unique(data[[facet_name]])
  plotlist <- lapply(seq_along(facet_vals), function(i) {
    v  <- facet_vals[i]
    df <- dplyr::filter(data, .data[[facet_name]] == v)
    if (nrow(df) == 0)
      return(NULL)
    local_title <- if (!is.null(plot_title))
      paste0(plot_title, ": ", v)
    else
      paste0(facet_name, ": ", v)
    is_left_col <- ((i - 1) %% facet_ncol) == 0
    build_one(df, local_title, show_y_titles = is_left_col)
  })
  plotlist <- Filter(Negate(is.null), plotlist)
  
  cowplot::plot_grid(plotlist = plotlist,
                     ncol = facet_ncol,
                     align = "hv")
}
```

## Distribution llm scores

This plot does not have any inference criteria. The only purpose of this plot is to see how scores are distributed generally.

```{r}
###! If I have no inference for this plot, should I even include them?
paper_llm_scores <- bar_function(
  dataset      = paper_llm_processed,
  base_cols    = BASE_SCORE_COLS,
  total_col    = TOTAL_SCORE_COL,
  clean_labels = CLEAN_SCORE_COLS
)

paper_llm_scores
```

## Distribution human scores

This plot does not have any inference criteria. The only purpose of this plot is to see how scores are distributed generally.

```{r}
paper_human_scores <- bar_function(
  dataset      = paper_human_processed,
  base_cols    = BASE_SCORE_COLS,
  total_col    = TOTAL_SCORE_COL,
  clean_labels = CLEAN_SCORE_COLS,
  suffix = "_human",
)

paper_human_scores
```

## Success rate

```{r}
success_spec_plot <- data_plot |>  
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyper-<br> parameter`, 
    `CoT<br> used`, 
    `Scope`, 
    success_rate,
    boot_success_lower,      
    boot_success_upper
  ) |>  
  # Summarize
  group_by(Model, `Hyper-<br> parameter`, `CoT<br> used`, Scope) |>
  summarise(
    success_rate = mean(success_rate),
    boot_success_lower = mean(boot_success_lower),
    boot_success_upper = mean(boot_success_upper),
    .groups = "drop"
  ) |> 
  arrange(success_rate) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
  outcome = success_rate,
  outcome_name = "Success rate TVD-MI",
  outcome_cutoff = 1.0,
  plot_title = "Specification Curve: Success rate by Configuration",
  interval_lower = "boot_success_lower",
  interval_upper = "boot_success_upper",
  rank_by = rank,
  
  mutate_plots = \(top, bottom, df) {
    list(top + coord_cartesian(ylim = c(0, 1)))
  }
)
```

This plot shows for how many papers in a given parameter combination the review generation was successful.

```{r}
success_spec_plot
```

## Mean

```{r}
###! The quality assessment ignores how many unsuccessful combos a configuration had. I have included this information via the transparency of the data point (alpha). Should I keep or drop this?

mean_spec_plot <- data_plot |> 
  # Preprocess
  dplyr::select(
    `Model`, 
    `Hyper-<br> parameter`, 
    `CoT<br> used`, 
    `Scope`, 
    group_mean,
    success_rate,
    boot_mean_lower, 
    boot_mean_upper,
    boot_mean_lower_human, 
    boot_mean_upper_human
  ) |> 
  # Summarize
  group_by(Model, `Hyper-<br> parameter`, `CoT<br> used`, Scope) |> 
  summarize(
    group_mean = mean(group_mean),
    success_rate = mean(success_rate),
    boot_mean_lower = mean(boot_mean_lower),
    boot_mean_upper = mean(boot_mean_upper),
    boot_mean_lower_human = mean(boot_mean_lower_human),
    boot_mean_upper_human = mean(boot_mean_upper_human),
    .groups = "drop"
  ) |> 
  arrange(group_mean) |>
  mutate(rank = row_number()) |> 
  # Plot call
  specification_curve_plot_with_shading(
    # Basic content
    outcome = group_mean,
    outcome_name = "Mean TVD-MI score",
    plot_title = "Specification Curve: Mean by Configuration",
    interval_lower = "boot_mean_lower",
    interval_upper = "boot_mean_upper",
    is_processed = success_rate,
    rank_by = rank,
    # CI base
    shade_lower = "boot_mean_lower_human",
    shade_upper = "boot_mean_upper_human",
    
    mutate_plots = \(top, bottom, df) {
      list(top + coord_cartesian(ylim = c(-1, 1)))
    }
  )
```

This plot indicates the average quality of LLM-authored reviews for each parameter combination. Note that this plot does not consider for how many of the papers the parameter combination yielded a review in the first place.

```{r}
mean_spec_plot
```

# Inferential tests

```{r}
# Function for conditional posthoc tests
conditional_posthoc_function <- function(model, alpha = 0.05, adjust = "bonferroni") {
  
  # Check if model is binomial (glmer) or linear (lmer)
  is_glmer <- inherits(model, "glmerMod")
  test_stat <- if(is_glmer) "Chisq" else "F"
  
  anova_res <- tryCatch({
    car::Anova(model, type = "II", test.statistic = test_stat)
  }, error = function(e) {
    message("ANOVA failed: ", e$message)
    return(NULL)
  })
  
  if(is.null(anova_res)) return(NULL)
  
  # Identify the p-value column (it's either Pr(>Chisq) or Pr(>F))
  p_col <- grep("Pr\\(>", colnames(anova_res), value = TRUE)
  
  # Handle cases where no terms are significant
  sig_mask <- anova_res[[p_col]] < alpha
  terms <- rownames(anova_res)[sig_mask]
  terms <- terms[!terms %in% c("(Intercept)", "Residuals")]
  
  if(length(terms) == 0) {
    message("No significant terms found at alpha ", alpha)
    return(list(anova = anova_res, posthoc = list()))
  }
  
  # Run post-hoc tests
  results <- lapply(terms, function(term) {

    spec_formula <- as.formula(paste("~", term))
    
    # Calculate Estimated Marginal Means
    emm <- emmeans::emmeans(model, specs = spec_formula, type = "response")
    
    # Compact Letter Display (CLD)
    multcomp::cld(emm, 
                  alpha = alpha, 
                  Letters = c(letters, LETTERS), 
                  adjust = adjust, 
                  reversed = TRUE) |> 
      as.data.frame() |> 
      mutate(term = term)
  })
  
  names(results) <- terms
  return(list(anova = anova_res, posthoc = results))
}
```

```{r}
###! By default the function deletes any combo which includes NAs. This can lead to bias, benefitial for combos with a small amount of kept rows, as my data is not missing at random. Can I still run them like this?

lmm_mean_total <- lme4::lmer(tvd_mi_score ~ model + hyperparameter + chain_of_thought + scope + (1 | paper_id),
                             data = paper_llm_processed)
posthoc_mean_total <- conditional_posthoc_function(lmm_mean_total, alpha = ALPHA, adjust = POST_HOC_CORRECTION)
```

```{r}
posthoc_mean_total
```

# Session info

```{r}
sessionInfo()
```

# References

::: {#refs}
:::
